\documentclass[11pt, letterpaper]{yt_resume}   	% use "amsart" instead of "article" for AMSLaTeX format

\begin{document}

\Name{Yu-Ting Shen}
\Phone{405.200.2633}
\Email{YuTing.Shen-1@ou.edu}
\LinkedIn{linkedin.com/in/yu-ting-shen-6b730b160}
\Github{github.com/ytatus94}

\header

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Qualifications}

% 主要分成四大類：學歷，程式/軟體，機器學習/統計/機率，資料庫，軟技巧
\begin{itemize}
\item Ph.D. degree in Physics with 5-years experience in data analysis, data visualization, machine learning, and statistics.
\item Strong programming skills in Python (pandas/numpy/scipy/scikit-learn/matplotlib/seaborn), R,  C/C++, and BASH shell script.
%\item Proficient in data manipulation using SQL and Pandas
%\item Experiences in Spark and knowledge of Hadoop and Hive.
\item Proficient in SQL, experiences in Spark, and knowledge of Hadoop and Hive.
\item Deep understanding of machine learning and hands-on experience in constructing and validating predictive models.
\item Advanced-level knowledge and daily experiences on using UNIX/Linux operating systems and Git version control.
\item Superior documentation and communication skills.
Ability to explain complex concepts to wide range of audiences.
\item Excellent analytic and problem-solving skills through critical thinking, teamwork with colleagues.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Project
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Projects}

%\subsection{Real Lepton Efficiency}{}{}{}{}
%\begin{itemize}
%\item Classified particles using decision tree based methods to improve the real lepton identification efficiency from 80\% to 98\%.
%\item Designed data filtration algorithms in C++ reducing the data size from $\sim$400 TB to less than 200 GB.%by a factor of 100.
%\item Developed a new framework to reduce the run time from one week manual operations to 5 hours automation.
%\end{itemize}
%
%\subsection{Capital Bikeshare Rental Demand}{}{}{}{}
%\begin{itemize}
%\item Performed feature selection and engineering to remove 3 standard deviations outliers and created new datetime features.
%\item Visualized the weather information and imputed missing data using the random forest model based estimation.
%\item Used random forest model to predict the total count of bikes rented during each hour of the last 10 days in each month.
%\end{itemize}
%
%\subsection{Upstart 3-year Terms Loan Charged-off Rate Prediction}{}{}{}{}
%\begin{itemize}
%\item Analyzed 50,000 loans with different repayment status within two years to extract the monthly default rate.
%\item Predicted the charged-off rate by the time all 3-year terms finished using linear regression.
%\end{itemize}
%
%\subsection{INSPIRE HEP PostDoc Position in North America}{}{}{}{}
%\begin{itemize}
%\item Scraped website using Beautiful Soup and converted results into SQL database using sqlalchemy.
%\item Leveraged natural language processing (NLP) and machine learning to predict institution participants in experiments.
%\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

% CERN
\subsection{Research Associate}{Organisation Europ\'{e}enne pour la Recherche Nucl\'{e}aire (CERN)}{Geneva, Switzerland}{2015 - 2018}
% \subsection{Research Assistant}{The European Organization for Nuclear Research (CERN)}{Geneva, Switzerland}{2015 - 2018}
\begin{itemize}
\item Performed data mining from the distributed LHC computing Grid using Python and BASH shell script.
\item Established data cleaning and processing pipeline to analyze data, visualize distributions, and select features.
\item Optimized the analysis processes and improved key performance metrics using decision tree algorithm.
\item Applied maximum likelihood fitting and statistical methods to extract signal within 95\% confidence interval.
\item Developed a method to calibrate the electron isolation efficiency and became the standard version of the collaboration.
\item Constructed classification model and improved the true positive rate of isolated electrons from 0.85 to 0.93.
\end{itemize}

% Academia Sinica
\subsection{Research Assistant}{Academia Sinica}{Taipei, Taiwan}{2009 - 2011}
\begin{itemize}
\item Discovered serious bugs in simulation programs by performing exploratory data analysis on simulated data.
\item Programmed in C++ to redesign a bug-free Monte Carlo simulation programs.
\item Devised a new classification model to improve the accuracy of signal and background identification.
\end{itemize}

% Taiwan Semiconductor Manufacturing Company
\subsection{R\&D engineer}{Taiwan Semiconductor Manufacturing Company}{Hsinchu, Taiwan}{2006 - 2009}
\begin{itemize}
\item Implemented regression algorithm for data fitting and validated model with advanced statistical method.
\item Programmed measurement system to automate data collection processes and reduced 30\% of manual-operation time.
\item Coordinated effectively with cross-functional teams and customers to resolve issues by tight deadlines.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\subsection{Real Lepton Efficiency}{}{}{}{}
\begin{itemize}
\item Built a predictive model to improve the significance of the signal of the real leptons.
\item Implemented statistical model and Monte Carlo method to predict the noises from various sources in the region of interest.
\item Enhanced the data-to-Monte Carlo from 80\% to 98\%.
\item Designed data filtration algorithms in C++ reducing the data size from $\sim$400 TB to less than 200 GB.
\item Developed a new framework to reduce the run time from one week manual operations to 5 hours automation.
\end{itemize}

\subsection{Uber churn rate prediction}{}{}{}{}
\begin{itemize}
\item
\end{itemize}

\subsection{Capital Bikeshare Rental Demand}{}{}{}{}
\begin{itemize}
\item Performed feature selection and engineering to remove 3 standard deviations outliers and created new datetime features.
\item Visualized the weather information and imputed missing data using the random forest model based estimation.
\item Used random forest model to predict the total count of bikes rented during each hour of the last 10 days in each month.
\end{itemize}

\subsection{Upstart 3-year Terms Loan Charged-off Rate Prediction}{}{}{}{}
\begin{itemize}
\item Analyzed 50,000 loans with different repayment status within two years to extract the monthly default rate.
\item Predicted the charged-off rate by the time all 3-year terms finished using linear regression.
\end{itemize}

%\subsection{INSPIRE HEP PostDoc Position in North America}
%\begin{itemize}
%\item Scraped website using Beautiful Soup and converted results into SQL database using sqlalchemy.
%\item Leveraged natural language processing (NLP) and machine learning to predict institution participants in experiments.
%\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

% University of Oklahoma
\subsection{Ph.D. in Physics}{University of Oklahoma}{Norman, OK}{Cum. GPA: 3.47 / 4.00}{2011 - 2018}
\begin{itemize}
\item Published 4 top journal papers and 5 conference notes, and presented in 2 conferences.
\item 6 semesters teaching assistant for college and graduate level courses.
\end{itemize}

% National Taiwan University
\subsection{M.S. in Physics}{National Taiwan University}{Taipei, Taiwan}{Cum. GPA: 3.86 / 4.00}{2003 - 2006}
\begin{itemize}
\item Won 3$^{rd}$ place graduate student thesis awards, The Physical Society of Taiwan, 2006.
\end{itemize}


\end{document}  