%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:https://www.overleaf.com/project/6392c372413f5d67d93b7245
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{hyperref}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Dr. Yu-Ting Shen} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
% \moveleft.5\hoffset\centerline{1588 Myrick Ct, San Jose, CA 95131} % Your address
% \moveleft.5\hoffset\centerline{}
\moveleft.5\hoffset\centerline{Mobile: (450)200-2633, E-mail: ytshen2020@gmail.com}
\moveleft.5\hoffset\centerline{LinkedIn: \url{https://www.linkedin.com/in/yu-ting-shen-6b730b160/}}

%----------------------------------------------------------------------------------------
% Descriptors command
\newcommand{\descript}[1]{\color{subheadings}\raggedright\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{12pt}{12pt}\selectfont {#1} \normalfont}

% Location command
% \newcommand{\location}[1]{\color{headings}\raggedright\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{12pt}\selectfont {\hfill #1\\} \normalfont}


\begin{resume}

%----------------------------------------------------------------------------------------
%	COUNTRY OF BIRTH SECTION
%----------------------------------------------------------------------------------------
\section{COUNTRY OF BIRTH}
\textbf{Taiwan}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION} 
\textbf{Ph.D. in Physics}\hfill{2011-2018}\\
\textbf{University of Oklahoma}\hfill{Norman, OK}\\
\begin{itemize}
    \item Advisor: Patrick Skubic
    \item Dissertation: Search for electroweak production of supersymmetric states in non-universal Higgs mass model with two extra parameters compressed scenario with the ATLAS detector
    \item Dissertation link: \url{https://hdl.handle.net/11244/299774}
\end{itemize}
\textbf{M.S. in Physics}\hfill{2003-2006}\\
\textbf{National Taiwan University}\hfill{Taipei, Taiwan}\\
\begin{itemize}
    \item Advisor: Paoti Chang
    \item Thesis: Measurements of branching fractions and CP asymmetries in $B \to \phi \phi K$ decays at Belle
    \item Thesis link: \url{http://www.airitilibrary.com/Publication/alDetailedMesh1?DocID=U0001-1407200616551200}
    \item GPA: 3.86/4.0
\end{itemize}
\textbf{B.S. in Physics}\hfill{1998-2002}\\
\textbf{Chung Yuan Christian University}\hfill{Chung Li, Taiwan}\\
\begin{itemize}
    \item Certification of Academic Achievement Award, year 2000-2001
    \item Certification of Holistic Achievement Award, year 2000-2001
    \item Certification of Holistic Achievement Award, year 1999-2000
    \item Certification of Holistic Achievement Award, year 1998-1999
    \item GPA: 3.53/4.0
\end{itemize}


%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{EXPERIENCE}
\textbf{Seeloz Inc.}\hfill{2019/04 - present}\\
\textbf{Senior Data Scientist}\hfill{San Jose, CA}\\
\textrm{Responsibilities}
\begin{itemize}
    % 領導三個不同的團隊，建立與維護 AI based SCAS (Supply Chain Automation Suite), order forecasting engine, 以及實時的儀表板 to support decision-making processes and drive data-driven strategies.
    \item Leading three different teams to create and maintain an AI-based Supply Chain Automation Suite (SCAS), an order forecasting engine, and real-time interactive dashboards to support decision-making processes and data-driven strategies for stakeholders.
    % 規劃與建立 data architecture 和 model architecture 使得分析 complex multi-stage supply chain 與監控實時 anomaly 變得更系統化與變得更容易
    \item Planning and designing data and model architectures made the analysis of complex multi-stage supply chain and real-time anomaly monitoring more systematic and easier. The efficiency is improved more than 50\%.
    \item Communicating with stakeholders to understand the business challenges and applying critical thinking and problem-solving skills to provide optimized recommendations or insights.
    \item Manipulating customers' supply chain data to analyze, built and trained machine learning models, statistical models, and other data-driven models to solve business problems and make predictions.
    % 負責面試過程，包括審核應徵者的履歷，篩選合適的應徵者並給予 take home exam 以考驗其數據分析與建立統計模型和機器學習模型的基礎能力，通過初步篩選的應徵者，我會負責協調與安排電話面試與 on-site 面試的時間，並且在面試時給予適當的面試問題，根據面試者的回覆我做專業並正確的評斷並且回報給 CTO 和 VP 供他們做選擇新成員時候的參考
    \item Participating in the interview process, I am responsible for reviewing resumes of candidates, screening suitable applicants by providing them with take-home exams to assess their data analysis, statistical modeling, and machine learning skills. Once the initial screening of candidates is done, I coordinate and schedule phone interviews and on-site interviews, and ask appropriate interview questions during the interviews. Based on the responses of the interviewees, I make professional and accurate evaluations, and provide feedback to the Chief Technology Officer (CTO) and Vice President (VP) for their reference in the selection of new team members.
\end{itemize}
\textrm{Expertise in Data Science}
\begin{itemize}
    % Basamh
    % 1. 分析阿拉伯大型連鎖超市 Basamh market 的歷史交易紀錄，建立實時儀表板與異常偵測系統，提取並分析造成異常倉儲水平的主要成因，幫助客戶降低 13% 的倉儲水平，節省了 inventory cost 並且增加了100萬的利潤
    % 2. 將 85 家超市分店5年來超過100M筆的銷售數據視覺化，提取出 KPI 並使用 Google DataStudio 將 data insights 轉換成 Business Intelligence (BI) 成為 stakeholder 做 data-driven decision-making 時的重要依據
    \item Analyzed the historical transaction records of Basamh market, a large chain supermarket in Arabia, and built business analysis reports and anomaly detection systems. Extracted and analyzed the root causes of abnormal inventory levels, helping the customer reduce inventory levels by 13\%, saving inventory costs, and increasing profits by \$1.2 million.
    \item Visualized sales data from over 100 million transactions spanning 5 years across 85 supermarket branches, extracted key performance indicators (KPIs), and transformed data insights into business intelligence (BI) using Google DataStudio. This became a crucial reference for stakeholders in making data-driven decisions.
    % Pharmaniaga
    % 1. 研究馬來西亞製藥公司, Pharmaniaga, 的 oracle database 內的數據，規劃 data architecture 以建立 SCAS meta data model 並與 data engineers 合作開發 ETL pipeline 將 oracle 資料格式轉換成 MDM 格式並且 部署在 google cloud platform 上
    \item Conducted research on Pharmaniaga's data, a pharmaceutical company in Malaysia. Designed the data architecture to create the SCAS Meta Data Model (MDM) and collaborated with data engineers to develop an ETL (Extract, Transform, Load) pipeline to convert the Oracle database format into MDM format, and deployed converted MDM data on the Google Cloud Platform. This MDM architecture later evolved into the industry standard for SCAS Autonomous Supply Chain Resource Planning.  
    % \item Domino's
    % 1. 與 data engineering team 合作建立為中東 Dominos pizza 特製的 ETL pipeline for on the Airflow. 這個 ETL pipeline 消除了將近 80% 的無用資料，並且也產生了 ~30% 的衍生數據，經過清理後的數據可以為 AP\&I 的執行效率顯著地提升 70\% 並且模型預測的準確度上升了 10\%
    \item Collaborated with the data engineering team to create a customized ETL pipeline for Domino's Pizza franchise in the Middle East. This ETL pipeline eliminated approximately 80\% of irrelevant data and generated around 30\% of derived data. After cleaning the data, it significantly improved the AP\&I model training efficiency by 70\% and results in \$1.3 million inventory value drop (from \$2.82 M to \$1.58 M) and annual turnover rate was increased 77\% (from 8.63 to 15.33).
    % \item Unifi
    % 1. 幫忙 global textile solutions company, Unifi, 建立一個涵蓋 12 個倉庫, 22882 商品 203 供應商 829 客戶的 的複雜網路分析，篩選出影響公司營收的 72 重要商品來建立機器學習模型。幫助 Unifi 在 2019 年上半年降低了 $1.44 million 的 COGS (Cost of Goods Sold), inventory value 下降了 27\% 並且 annual turnover rate 上升了 23\%
    \item Built a complex network analysis covering 12 warehouses, 22,882 products, 203 suppliers, and 829 customers for Unifi, a global textile solutions company. Through this analysis, 72 key products that significantly impact the company's revenue were identified and were used to build machine learning model. With the assistance of the model, Unifi was able to reduce Cost of Goods Sold (COGS) by \$1.44 million (from \$20.95 M to \$19.51 M) in the first half of 2019. Additionally, inventory value decreased by 27\% (from \$7.32 M to \$5.35 M), and the annual turnover rate increased by 23\% (from 5.56 to 6.83).
    \item Conducted comprehensive time series analysis and forecasting on over 2000 products from Unifi, utilizing a diverse range of modeling techniques including statistical models such as ARIMA, Exponential Smoothing and Prophet, machine learning models such as Random Forest, XGBoost, and LightBGM, as well as a deep learning model like LSTM. 
    % \item Ingress
    % 1. 應用高階統計分析來研究馬來西雅汽車零件製造商 ingress 各類商品的 lead time 與 safety stock 並且引入動態安全庫存的新概念，使得增強式學習的 AI 模型經過 3 百萬次訓練後成功地將各類商品的 stock outs 和 lost sales 降低了 8% ~ 22% 
    % 2. 引入複雜深層神經網路來最佳化庫存管理與供應鏈效率的增強式學習模型，降低了年平均庫存水平 26% (從 \$7.82M 到 \$5.77M) 並且年度翻桌率上升了 44\% (從 15.42 到 22.27).
    % 3. 針對 sparse data 的 demand forecast 開發全新的時間序列預測模型以解決發散性的問題，，使用兩個 random forest 模型來預測，並且加入 rolling windows 與 postpone action, 使得 MAE 下降了 68%
    % 4. 設計出一款基於 python 的實時監控儀表板，支援檢測模型組態參數，將原始數據轉換成圖表供初步分析與異常偵測，可將AI模型預測的結果與歷史數據擬合併比對，擷取
    \item Conducted high-level statistical analysis methods to study the lead time and safety stock of products from the auto parts manufacturer, Ingress, in Malaysia. Introduced a new concept of dynamic safety stock into the reinforcement learning model to train AI agent 3 million iterations, as a result, the stock outs and lost sales were successfully reduced by 8\% to 22\% across products.
    \item Developed a new time series forecasting model specifically for sparse demand data to resolve the issue of divergence by leveraging a double random forest model with postponed action and accomplished a 68\% reduction in MAE (Mean Absolute Error).
    \item Designed a Python-based monitoring dashboard that supports listing model configuration parameters, converting raw data into charts and tables for preliminary analysis and anomaly detection. The dashboard is capable of comparing the results of AI model predictions with historical data to identify the improvements.
    % \item Aramco
    % 1. 為 SCAS 的 oil supply planning and scheduling (OSPAS) 設計資料結構，使 SCAS 支援autonomously optimized upstream oil & gas operations with minimized waste, enhanced ability to handle demand fluctuations and maximized sustainability.
    % 2. 開發數據驅動的 AI 決策模型，使用全球最大的石油公司的數據聚焦供應鏈管理與優化庫存，模型提供了從煉油廠到散裝廠運輸油的最佳時間、體積、流量和泵送速率的優化方案以滿足兩個 bulk plant 的客戶端需求，實現 bulk plant 低庫存水平，並將整個系統的成本最小化。
    % 3. 
    \item Designed data architecture for oil supply planning and scheduling (OSPAS) to enhance SCAS functionality, enabling autonomous optimization of upstream oil and gas operations, minimizing waste, enhancing ability to handle demand fluctuations, and maximizing sustainability.
    \item Focused on supply chain management and optimized inventory control to meet customer demands for two bulk plants of the world's largest oil company, Aramco. The goal was to achieve low inventory levels at the bulk plants while minimizing the overall system costs. The system includes one refinery, two bulk plants, one strategic storage depot, four pipelines, and two customers at bulk plant side.
    % \item 該項目的重點是利用沙特阿拉伯全球最大的石油公司的數據，聚焦供應鏈管理和庫存優化。主要目標是滿足兩個散裝廠的需求，實現每個散裝廠低庫存水平，並將整個系統的成本最小化，該系統包括一個煉油廠、兩個散裝廠、一個戰略性儲存庫、四條管道和兩個客戶。為了實現這一目標，我首先設計了數據架構並定義了元數據模型，以確定所需的數據和格式。然後，我創建了SQL查詢和Python腳本，從SAP和iMDAD數據庫中提取和清理數據。通過分析各種因素，如油種類、管道流量、運輸限制以及煉油廠和客戶端的供需情況，我開發了一個強化學習模型來進行決策。該模型提供了從煉油廠到散裝廠運輸油的最佳時間、體積、流量和泵送速率的優化方案。我利用三年的歷史數據來訓練模型，然後用它來預測未來90天的最佳油品運輸計劃。結果顯示，未滿足的需求低於3％，平均庫存水平比目標水平低4.8％，總成本降低了7.9％。最後，我使用Python中的Dash包創建了一個交互式儀表板，用於可視化歷史數據和模型結果，包括11個關鍵績效指標、8個表格和6個圖表供利益相關者使用。此儀表板已打包為Docker容器以部署在客戶端的本地群集上，以保護其機密數據。
    

%     \item turnover 上升了 50-80% average inventory 下降了 20-40% stockout 降低 40=70% cross warehouse movement 降低了 30-60%
%     \item production
%     \item distribution
%     \item mro intelligent MRO (Maintenance, repair, and operation)
%     \item ospas
%     \item Autonomous Procurement
% & Inventory (AP&I)
% \item Minimize Inventory Days to free tied up Capital
% holistically analyze millions of SKUs concurrently,
% Anomaly Detection & Root Cause Analysis
% cross supply chain analysis for cost reductions
% complex multi-stage manufacturing supply chain
% planned replenishment orders (procurement), work orders (manufacturing plan), and transfer orders (cross warehouse movement)
% minimize inbound supply chain cost, optimize production efficiency, maximize outbound reliability and efficiency
\end{itemize}
\textrm{Developments}
\begin{itemize}
    % csv_to_parquet
    % 建立一個資料擷取與轉換工具，能把 sap 或是 oracle 資料庫中 GB 級別的原始資料轉換成 highly efficient column-wise compression, and flexible encoding schemes format helped to reduce storage requirements by at least one-third on large datasets, in addition, it greatly improved scan and deserialization time, hence the overall costs.
    \item Created a data extraction and transformation tool that can convert Gigabytes-level raw data from SAP or Oracle databases into a highly efficient column-wise compression format with flexible encoding schemes. This format has helped to reduce storage requirements by at least 30\% on large datasets, in addition to significantly improving scan and deserialization time, resulting in overall cost savings on cloud storages.
    % config_generator
    % CloudIO
    \item Developed an Python API (Application Programming Interface) offers cross-platform capabilities for accessing cloud storages on GCP, Azure, and AWS. This API was adopted in all Seeloz products and significantly enhanced workflows' efficiency and functionality.
    % TraditionalSupplyChain
    % 獨立開發出基於供應鏈管理理論的 EOQ 模型 ROP 模型，TPOP 模型，並且將其整合至 AP&I 裡面以擴充 AP&I 的功能使得支援的模型種類增加了 4 倍。
    \item Developed independently EOQ (Economic Order Quantity), ROP (Reorder Point), and TPOP (Time Phase Ordering Point) models based on supply chain management theories, and integrated them into AP\&I framework to expand its functionality, resulting in a fourfold increase in the supported model types.
    \item Developed the traditional supply chain management model which reduces the execution time from 5 hours to 2 minutes.
    % inspector
    % singlewarehouse & multiechelon & APNI
    % 在 stable baseline frame 中使用增強式學習建立單倉庫單產品的機器學習模型，設定增強式學習 agent 與 environment 的交互作用與 reward 反饋機制，並且使用 Pharmaniaga 的歷史數據來訓練增強式學習的模型，使得 agent 可以基於狀態函數和指定的 policy 預測產品庫存趨勢，並且採取適當 action 以避免庫存過高造成高成本與庫存過低造成 stock outs 的情形
    \item Built a machine learning model using reinforcement learning in the stable-baseline framework to optimize inventory control and management for a single warehouse and single product. Configured the interactions between the reinforcement learning agent and the environment, including the reward feedback mechanism. Utilized historical data from Pharmaniaga to train the reinforcement learning model. After training for 5 million steps on Google AI platform, the agent was able to predict product inventory trends based on state functions and the specified policy, and made decisions and took appropriate actions to avoid excessive inventory resulting in high costs or lost sales due to stock-outs.
    % 改進 single warehouse and single product 的 reinforcement learning 並設計與實作出多個 warehouses and single product 版本的 reinforcement learning model, multi-echelon. Multi-echelon 考慮到 warehouses 之間複雜的網路關係，並採用 deep learning neutral network 來計算 Q-value
    \item Improved the reinforcement learning model for single warehouse and single product, and designed and implemented a multi-echelon version of the reinforcement learning model for multiple warehouses and a single product. The multi-echelon model takes into account the complex network relationships between warehouses and utilizes deep learning neural networks to compute Q-values.
    \item Integrated the reinforcement learning based models for single warehouse single product and complex network multi-warehouse single product into the AP\&I (Autonomous Procurement \& Inventory) framework.
    % singlewarehouse_dashboard
    % timeseries_analysis and Demand_Forecast
    % inputargs
    % dashboard_apni_prep
\end{itemize}
\textrm{Leadership}
\begin{itemize}
    % \item 領導三個不同的團隊，團隊成員分佈於美國加州與德州，馬來西亞，和巴基斯坦。負責開發與維護世界上第一個基於人工智慧的 Autonomous Requirements Planning (ARP) Engine which can reduce the inefficiencies throughout the supply chain，monitors the supply chain to detect anomalies, provide root cause analysis, derive actionable insights, and recommend corrective actions
    \item Led a team of 8 data scientists, responsible for developing and maintaining the world's first Artificial Intelligence-based Autonomous Requirements Planning (ARP) engine, which is capable of reducing inefficiencies throughout the entire supply chain. The engine monitors the supply chain to detect anomalies, provides root cause analysis, derives actionable insights, and recommends corrective actions.
    % \item 領導一個三人團隊建構 model architecture 開發訂單需求預測引擎 at scale，為客戶端90天內的訂單需求提供了最佳解決方案。此訂單需求預測引擎混合了時間序列的 SARIMA 模型與 Holt-Winters Exponential Smoothing 統計模型與機器學習的隨機森林模型和 XGBoost 還有深度學習的 LSTM 模型，使得可預測商品的數量上升了超過 100 倍，並且預測結果的精準度提高了 30%-70%
    \item Led a three-person team to design model architecture and build a scalable order forecasting engine, providing optimal solutions for customer's order within 90 days. This order forecasting engine combines time series SARIMA model, Holt-Winters exponential smoothing statistical model, machine learning random forest and XGBoost model, and deep learning Long-Short Term Memory (LSTM) model. As a result, the ability to predict the variety of products increased by over 100 times, and the accuracy of the forecasting results improved by 30\%-70\%, varying depending on the type of products.
    % \item 指導新進的資料科學家基礎供應鏈的相關知識，如何從事供應鏈的數據清洗與分析，以及使用客戶數據建立機器學習與增強式學習的模型
    \item Provided guidance to junior data scientists on foundational knowledge of the supply chain, data cleaning and analysis technologies for supply chain data, as well as building machine learning and reinforcement learning models using customers' supply chain data.
    % \item 協助指導資料工程師建立一鍵式供應鏈數據清洗，轉換，與提取的作業流程，並且在 airflow 上架設此作業流程
    \item As a leader based at the headquarters in Santa Clara, with team members located in Texas, Malaysia, and Pakistan, I am responsible for conducting daily meetings to understand the progress of each team member's work, providing guidance and suggestions, and offering technical support with professional expertise to demonstrate my ability to coordinate and manage members globally.
\end{itemize}


\textbf{CERN (Organisation Européenne pour la Recherche Nucléaire )}\\
\textbf{Data Scientist}\hfill{2015/03 - 2018/03, Geneva, Switzerland}\\
\textrm{Responsibilities}
\begin{itemize}
    % 主導 isolation electron efficiency measurement 的研究，採用 tag-and-probe 技術分析 z->ee 通道中的電子事件來研究 isolation electron 的特性，因此可利用 isolation electrons 來幫助區分訊號與背景事件
    \item Led the isolated electron efficiency measurement. Developed and performed the tag-and-probe technique on the $Z \rightarrow ee$ decay channel to study the properties of the isolated electrons at $\sqrt{s} = 13$ TeV with the ATLAS detector.
    \item Devised an asymmetrical matrix approach for isolated electron working points that integrates static and dynamic working points for 24 combinations spanning a transverse energy ($E_{T}$) range of 150 GeV, achieving an efficiency of up to 99\% for isolated electrons.
    \item Searched for strongly-produced supersymmetric particles in final states with two same-sign or three leptons and jets, and weak production of compressed supersymmetry with two soft leptons and missing transverse momentum $p_{T}^{miss}$ using 36 fb$^{-1}$ of $\sqrt{s} = 13$ TeV proton-proton collision data.% with the ATLAS detector. 
    \item Led the measurement of the data-driven real lepton efficiency and developed a new background template method to model the background contamination on data.
    \item Searched for electroweak production of supersymmetric state in Non-Universal Higgs Mass model (NUHM2) with 2 extra parameters compressed scenario.
    % \item 負責 real lepton efficiency 的測量
    % \item Same sign or three leptons and jets
    % \item NUMH2
\end{itemize}
\textrm{Expertise in Data Science and Particle Physics}
\begin{itemize}
    % 1. 在  Worldwide LHC Computing Grid (WLCG)  上做資料探勘，從分布在全球 42 個國家超過 170 機構約 1.5 exabytes 的龐大實驗數據中，篩選出約 400 TB 符合 same sign or 3 leptons and jets 的事件。
    % 2. 使用 C++ 與 Bash shell script 來編寫 ETL 程式，從 400 TB 的海量數據中，擷取出有效數據並且轉換成高能物理研究所使用的 Root 格式
    \item Leveraged exceptional expertise to conduct data mining on the extensive ATLAS experimental data, which exceeds 1.5 exabytes ($1.5 \times 10^9$ GB) and is distributed across more than 170 institutions in 42 countries within the Worldwide LHC Computing Grid (WLCG).
    \item Developed a powerful ETL (Extract, Transform, Load) program using C++ and Bash shell scripts, capable of efficiently extracting valuable datasets and transforming them into the required ROOT format for high-energy physics research. This ETL program can reduce the data size from $1.5 \times 10^{9}$ GB to $4 \times 10^5$ GB (400 terabytes), corresponding to 99.97\% reduction rate, within 5 hours. 
    % massive 400 terabytes ($4 \times 10^5$ GB) datasets. This work demanded profound technical expertise and rich domain knowledge in the field of high-energy physics, showcasing outstanding technical talent and excellent programming skills.
    \item Performed Monte Carlo simulations of the electron-rich physics processes in $Z \rightarrow ee$ decay channel using C++, ROOT. Successfully implemented the tag-and-probe method to classify tag electrons and probe electrons, with accuracy 98\% $\sim$ 99\%, by utilizing the decision tree algorithm and $Z$ invariant mass window around 91 GeV/$c^2$.
    \item Categorized isolated electrons into 8 categories with 3 isolation levels in each category using the sum of transverse energies of topological clusters $E_{T}^{cone 0.2}$ and the sum of transverse momenta of all tracks $p_{T}^{varcone 0.2}$ around the candidate electron track and originating from the reconstructed primary vertex of the hard collision.
    \item Reconstructed two same-sign or three leptons with jets candidates using the 36 fb$^{-1}$ proton-proton collision data collected at the ATLAS detector in 2015 and 2016 and performed object selections based on the kinematic, identification, isolation, impact parameter, clustering, pileup mitigation  and $b$-tagging.
    \item Analyzed data for irreducible background, which mainly come from diboson $VV$ and $t\bar{t}V$, and reducible background, which come from charge-flip and fake non-prompt leptons, to build statistical models to estimate the background contamination and validate with dedicated validation regions VRs.
    \item Excluded the $m_{1/2} < 650$ GeV region with 95\% confidence levels on the cross-section $\sigma$ as a function of $m_{1/2}$ in the NUHM2 model by analyzing the signal region SR and compare with the Standard Model predicted $pp \rightarrow \tilde{g}\tilde{g}$ process.
    \item Developed a new data-driven background template method to estimate the low $p_{T}$ leptons to extract the high purity of prompt leptons using the data generated by the  $Z \rightarrow \ell\ell$ process. Found the prompt lepton contamination ranging from 0.44\% to 4.04\% for various $p_{T}$ and pseudorapidity $\eta$.
    \item Derived the real lepton efficiency as a function of $p_{T}$, $|\eta|$ and $\Delta R(\ell, jet)$, where $p_{T}$ ranging from 0 to 200 GeV, $|\eta| < 2.01$ with crack region removal, and $\Delta R(\ell, jet) < 0.4$.
    \item Implemented the NUHM2 model with $m_{0} = 5$ TeV, $m_{A} = 1$ TeV, $A_{0} = -1.6 m_{0}$, $\tan\beta = 15$ and $\mu = 150$ GeV in ISAJET and PROSPINO to generated SUSY signal MC samples with $m_{1/2}$ ranging from 350 GeV to 800 GeV and produced the mass spectra of charginos $\tilde{\chi}^{\pm}_{1,2}$ and neutralinos $\tilde{\chi}^{0}_{1,2,3,4}$, and mass splitting spectra of electroweakinos.
    \item Analyzed MC and experimental data to build statistical model for identifying and reconstructing electrons, muons, and jets candidates. The signal candidates are further improved by utilizing discriminating variables to suppress $\sim$98\% backgrounds.
    \item Extended the cross section upper limit to $\sigma_{UL} = 11.5$ and $3.8$ pb for $m_{1/2}=350$ GeV and $m_{1/2}=800$ GeV for the NUHM2 scenario with 95\% CL.
%     \item 發展新的研究方法，利用 Z->ee 與 Tag-and-probe 方法來研究 isolated electrons efficiency. 把電子施加 Strict selection criteria 篩選出作為 tag 的電子候選人，再利用  invariant mass window provide a loose pre-identification of the other electron candidate (“probe”)，並且只使用 probe 電子做研究
%     \item implement electron identification (ID) algorithms are used to distinguish signal or background-like candidates based on multivariate likelihood discriminant 然後將電子區分成 Tight, Medium, and Loose三個類別
%     \item 發展出 isolation electron 的方式 a calorimetric isolation energy Econe 0.2
% T and a track isolation pvarcone 0.2
% T  利用 energy deposited in a cone centered around the electron candidate
%     \item 靜態與動態 isolation electron working points, 靜態可以
%     \item isolation electron 可以有效的降低 background
%     \item 用 C++ 物件導向重新編寫 real lepton efficiency 取代舊的 C 風格的程式，優化了程式的執行效率並且支援了更多的數據量
\end{itemize}
\textrm{Research Achievement}
\begin{itemize}
    % 變成 ATLAS collaboration 在 electron isolation 研究方面的專家，在 2015 年受邀請到法國安息的 Laboratoire d'Annecy de Physique des Particules 舉辦的 ATLAS e/gamma workshop 演講，又在 2016 年受邀到希臘 hessaloniki 的會議上演講。
    % 我的研究成果在電子隔離方面的研究成果已成為ATLAS協作中的標準，所有與電子相關的研究主題都採用了我的研究結果。因此，在近400篇期刊論文中，都引用了我的研究結果來進行他們的分析。
    % 在五個 conference 發表研究成果, 並有 18 篇 ATLAS 內部論文
    \item Completed the training at the ATLAS Control Center and became a qualified experiment monitor, responsible for monitoring the operation of the calorimeters (including the Electromagnetic calorimeter, Hadronic calorimeter, and Forward calorimeter) in the ATLAS experiment.
    \item Became an expert in electron isolation research within the ATLAS collaboration, and was invited to give a presentation at the ATLAS e/gamma workshop held at Laboratoire d'Annecy de Physique des Particules (LAPP) in France in 2015, and again invited to speak at a conference in Thessaloniki, Greece in 2016.
    \item My research findings on isolated electron efficiency measurement have become the standard within the ATLAS collaboration, and have been adopted in nearly 400 research topics which electrons participate in the interaction.
    \item Presented my research findings in isolated electron efficiency, real lepton efficiency, and supersymmetric particles at 5 conferences and have published 18 ATLAS internal papers.
\end{itemize}
\textrm{Leadership}
\begin{itemize}
    % 指導英國格拉斯克大學的博士生從事 electron isolation 的研究
    % 作為 NUHM2 的主要研究者，使 OU 成為這一個研究題目的領導
    \item Supervised a doctoral student at the University of Glasgow in research on isolated electron efficiency measurement.
    \item As the primary researcher of the Non-Universal Higgs Mass model with 2 extra parameters (NUHM2) project, I have led University of Oklahoma in becoming a leader in this research topic.
\end{itemize}

% \begin{itemize}
    % \item 參與 ATLAS 實驗，主要研究方向是超對稱模型，
    % \item Electron Isolation 
    % \item Real lepton efficient
    % \item NUHM2
    % \item 分析了 30,000,000 以上的事件，使得 isolation electron 的 tPR 從 0.85 上升到 0.93 而且這個 electron isolation efficiency callibration 變成了 ATLAS 的標準，所有 ATLAS 的研究只要有使用到 electron 的都需要引用我的結果去做校正
    % \item 使用決策數的方法來最大化 significance 並且把 data selection 過程最佳化
    % \item 建立資料清洗和數據分析的 pipeline 然後做 unbinned maximum likelihood fit 來抽取出信號在 95% confidence level 區間
    % \item 建立並且最佳化資料分析的 pipeline 降低了 80% 的 CPU 時間並且增加了 key performance metrics
    % \item 使用 python 來建立決策樹還有回歸模型給整個分析團隊使用
    % \item 建立回歸模型並且應用統計學方法來抽出數據，在95%的信賴區間中
    % \item 把 true positive rate 從 0.85 上升到 0.93 藉由發展新的 classification model 給 electron isolation efficiency 然後變成了 ATLAS 的標準
    % \item
% \end{itemize}


\textbf{University of Oklahoma}\\
\textbf{PostDoc Research}\hfill{2018/05-2019/04, Norman, OK}\\
\begin{itemize}
    % \item 繼續研究超對稱模型 NUHM2 和西班牙瓦倫西亞大學，美國路易斯安那理工LOUISIANA TECH合作，並且為 OU 建立在此研究題目上的領導地位
    \item Continued research on the Non-Universal Higgs Mass Model with 2 extra parameters (NUHM2) to search strong interaction and weak interaction supersymmetric particles in collaboration with the University of Valencia in Spain and Louisiana Tech University in the United States, and establish University of Oklahoma leadership position in this research topic.
    % \item 將 ou 高能物理研究團隊的研究成果整理並作成研究摘要的海報，作為向 DOE 申請三年的研究經費grant 的 proposal 文件之一
    \item Compiled the research achievements of the University of Oklahoma High Energy Physics group and created a research abstract poster as one of the proposal documents for applying for a three-year  grant from the department of energy.
\end{itemize}
\textbf{Graduate Research Assistant}\hfill{2013/08-2015/03, Norman, OK}\\
\begin{itemize}
    % \item 擔任團隊中主要的數據分析研究角色，分析 ATLAS 實驗數據，主要在研究超對成模型，包括與法國博士後研究人員，還有美國理論學家一起研究 NUHM2，擔任團隊中主要的數據分析研究角色
    \item Analyzed ATLAS experimental data, mainly focusing on the supersymmetric particles research, including collaborating with French postdoctoral researchers and theoretical physicists in the United States, and serving as the primary role of data analysis in the team.
    % \item 指導新進的博士生如何在他們的數據分析專案上使用 C++, python, 和 root 建立數據分析的流程與模型
    \item Supervised new doctoral students on how to use C++, Python, and ROOT to establish data analysis pipelines and build particle classification models for their data analysis projects.
    \item Because of outstanding research abilities, I was selected by my advisor to be a doctoral researcher and data scientist located at the European Organization for Nuclear Research (CERN) in Swiss for research in supersymmetric particle physics. At CERN, I participated in E/$\gamma$ and same-sign diboson supersymmetry physics research groups with the ATLAS experiment and was responsible for data analysis, experimental monitoring, and result reporting. I also attended many international conferences and seminars, exchanging ideas and the latest research results with other researchers. My work was highly praised by international peers and published in several well-known physics journals.
\end{itemize}
\textbf{Graduate Teaching Assistant}\hfill{2011/08-2013/08, Norman, OK}\\
\begin{itemize}
    % \item Graduate Teaching Assistant 6 個學期的 TA 大學和研究所的，課程包括基礎物理1, 2，量子物理 1, 2，固態物理 1, 量子力學 1, 2, 物理與生活
    \item Graduate Teaching Assistant for 6 semesters in both undergraduate and graduate courses. These courses included Fundamental Physics 1 and 2, Quantum Physics 1 and 2, Solid State Physics 1, Quantum Mechanics 1 and 2, and Physics and Life. Helped professors to grade undergraduate and graduate students homework, exams and tutored students in lecture hours.
\end{itemize}

% \begin{itemize}
%     \item DOE poster
%     \item Research relocated to CERN to search supersymmetric particles
%     \item Courses
    
%     % \item 研究超過 1,000,000 的實驗數據，來增強模型預測的精確度，用來發現動量與 true positive rate 之間的關係
%     % \item 產生 MC 模擬的數據，並且用特徵工程抽出有用的特征
% \end{itemize}


\textbf{Academia Sinica}\hfill{2009/07-2011/07}\\
\textbf{Research Scientist}\\
\textrm{Responsibilities}
\begin{itemize}
    % \item 參與 TEXONO 實驗，實驗主要在研究 low energy neutrino and dark matter physics 我所負責的事情包括實驗的制冷系統的維護，架構遠端數據的管道，設計 mc simulation 的程序，分析數據與建立模型來抽取出訊號，協助資料庫的建立，以及指導新進人員
    \item Participated in the TEXONO experiment, which mainly focuses on researching low energy neutrino and dark matter physics. My responsibilities include maintaining the experiment's cooling system, constructing the pipeline for remote data management and access, developing programs for Monte Carlo (MC) simulation, analyzing data to build statistical and machine learning model and extract signal, assisting in the establishment of the database, and guiding new team members.
\end{itemize}
\textrm{Expertise in Data Science}
\begin{itemize}
    % \item 藉由 exploratory data analysis 的分析手法發現了現有的 mc 模擬程式中存在著嚴重的 bug
    % \item 發現了 MC 模擬程式中有嚴重的 bug，所以重新用 C++ 與 GEANT4 寫了一個高純度鍺探測器的模擬程式，用來模擬在實驗環境中帶電粒子與不帶電粒子在通過鍺探測器時，所有可能的物理反應
    \item Used exploratory data analysis techniques to analyze the experiment data and discovered serious bugs in the existing Monte Carlo (MC) simulation program. Therefore, I rewrote a new bug-free MC simulation program for high-purity germanium detector using C++ and GEANT4, which simulates all possible physical reactions of charged and uncharged particles passing through a germanium detector in the experimental environment. The new MC simulation program significantly improved the simulation accuracy by 70\%.
    % \item 實作最新的決策樹方法來建立機器學習模型 for classification 來區分信號與背景，此一方法降低了50%的背景雜訊，使得 signal significance s/sqrt(s+b) 有顯著的上升
    % \item 使用新的 classification model 使得 signal significance 上升了 50%
    \item Implemented the cutting-edge decision tree method to create machine learning classification models to distinguish between signal and background events. This method reduced 50\% $\sim$ 80\% of the background noise, resulting in a significant increase in signal significance and figure of merit (FOM) in the sub-keV energy region.
    \item Implemented and optimized various selection criteria, for example, cosmic ray vetos and anti compton vetos, and charged particle positions resulting in 90\% of suppression factor.
    \item Conducted thorough study of underground neutrino experiments worldwide and incorporated the data analysis techniques used in those experiments into the TEXONO experiment, resulting in the number of signal event candidates increased by an order of magnitude.
\end{itemize}
\textrm{Experiment Setups}
\begin{itemize}
    % \item 被指導教授派到中國錦屏極深地下暗物質實驗室 china jinping underground laboratory 協助北京清華大學建立與 TEXONO 實驗類似的微中子實驗設施
    \item Invited to the China Jinping Underground Laboratory (CJPL) for Dark Matter Experiments in Sichuan, China to assist Tsinghua University in establishing a neutrino experiment facility similar to the TEXONO experiment. Helped Tsinghua University to design and build a Cosmic Ray Veto system which recorded a factor of two improvement for cosmic ray background suppression.
    \item Installed detachable shielding structure made of OFHC copper for the anti-Compton detectors.
    % \item 和政府機關，電信廠商，核能電廠協商溝通，建立一條專屬於 TEXONO 實驗的數據通道，方便實驗人員遠端存取操控實驗設施
    \item Negotiated and communicated with Kuo-Sheng power plant, telecommunications companies, and power plants to establish a dedicated data channel exclusively for the TEXONO experiment, facilitating remote access and control of the experimental facility by the research team at Academia Sinica.
    % \item 協助資料工程師建立磁碟陣列與資料庫，用以保存實驗數據
    \item Assisted data engineers in setting up RAID (redundant array of independent disks) disk arrays and constructed NoSQL databases to store the TEXONO experimental data.
\end{itemize}
\textrm{Leadership}
\begin{itemize}
    % \item 指導新來的印度籍博士生與天津大學的交換碩士學生如何做數據分析
    \item Supervised a new Indian doctoral student and an exchange master's student from Tianjin University on how to perform data analysis for the TEXONO experiment.
    \item Led a team for maintaining the cooling system for the TEXONO experiment and cross functional communicated between the liquid nitrogen manufacturer and Kuo-Sheng power plant for cooling schedule plan.
\end{itemize}


\textbf{TSMC (Taiwan Semiconductor Manufacturing Company)}\hfill{2006/12-2009/02}\\
\textbf{R\&D Engineer}\\
\textrm{Responsibilities}
\begin{itemize}
    % \item 曾經領導了 7 個專案，主要工作內容是負責各種 high voltage 的電子元件，主要包含了 MOSEFET, BJT, Diode, Capacitor, Resistor 的實驗的建立，實驗數據的收集，與建立電路模型來預測各種元件在各種工作條件下的 performance 。並把實驗的測量結果與模型結果視覺化為圖表，並且寫說明文件，詳細說明每個電子元件的 spec 工作範圍，運用場合，並且對客戶提供了技術支援
    \item Led 7 projects in which my main responsibilities included establishing experiments for high-voltage integrated circuit devices, collecting experimental data for data analysis, and creating circuit models to predict the performance of various high-voltage integrated circuit devices, such as MOSEFET, BJT, Diode, Capacitor, Resistor, and Back-end, under various operating conditions.
    \item Visualized the experimental and model results as graphs and wrote explanatory documents detailing the specifications, operating ranges, and usage scenarios of each electronic component.
    \item Created knowledge database, standard operating procedures (SOP) and automate the modeling steps for the department.
    \item Provided technical support to company’s clients and other department.
\end{itemize}
\textrm{Expertise in Data Science}
\begin{itemize}
    % \item 用 Excel VBA 開發數據分析的 pipeline 把數據分析流程自動化，所以降低了 5% ~ 10% 因人為造成的的模型 variance 並且教導同事如何把此 pipeline 導入到他們正在執行的專案中
    \item Developed a data analysis pipeline using Excel VBA to automate the data analysis process, reducing the model variance caused by human error by 5\% $\sim$ 10\%. And taught my colleagues how to implement this pipeline into their ongoing projects. This data analysis process pipeline successfully improved 30\% $\sim$ 50\% productivity efficiency.
    \item Independently created C++ programs to build regression models to fit the capacitor and resistor experimental data in Unix operation system and release the programs to the team members. This program dramatically reduced the capacitor and resistor models delivery time form 2 days to 5 hours.
    % \item 利用 high level statistical methods 來建立電子元件的統計模型，使得模型預測的結果落於 95% 信賴區間
    \item Built BSIM4 models for MOSFET and BJT to extract model parameters and used high-level statistical methods to build statistical models for various electronic devices, ensuring that the model's predicted results fall within a 95\% confidence interval.
\end{itemize}
\textrm{Experiment Setups}
\begin{itemize}
    % \item 幫助廠商安裝量測機台，測試機台的運作並驗收，為機台寫自動化測試程式，加入排程，使得機器能迅速找到正確的量測元件，並且開始自動測量，節省了約 30% 的測量時間，寫測量元件的 sop
    % \item Helped equipment manufacturer to install two new probe stations in the laboratory and validated the probe stations operate as expected.
    \item Assisted manufacturers in installing two probe stations for measurement in two laboratory, testing the equipment's operation, and accepting the equipment after passing the test.
    \item Wrote automated testing programs for the probe station, including scheduling and device patterns finding, to enable the probe station to quickly locate the correct measuring components and begin automated measurements, saving approximately 30\% of measurement time.
    \item Created standard operating procedures (SOP) for measuring components. Then this SOP became the department standard and all the team members have to follow the SOP for the measurement.
\end{itemize}
\textrm{Leadership}
\begin{itemize}
    % \item 七個專案的專案負責人，負責跨部門的溝通協商，安排會議與分配資源給專案，討論專案 SCOPE 元件模型的 SPEC，曾經負責過的專案包括使用 0.13 um, 0.18 um, 0.20 um, 0.25 um, 0.35 um, 0.6 um 0.99 um 半導體製程的 mix-mode 與 BCD HV SPICE Model projects
    \item Project manager for seven important projects, was responsible for cross-departmental communication and negotiation, arranging meetings, and allocating resources to the projects. Discussed the scope and models' specifications for each project with different departments and clients. The projects I have managed included mix-mode and BCD HV SPICE Model projects using the state-of-the-art semiconductor processes such as 0.13 $\mu$m, 0.18 $\mu$m, 0.20 $\mu$m, 0.25 $\mu$m, 0.35 $\mu$m, 0.6 $\mu$m, and 0.99 $\mu$m
    % \item lead engineer in High-Voltage SPICE (Simulation Program with Integrated Circuit Emphasis) team, 為實驗量測，數據分析與建立模型，文件撰寫開發了許多標準作業流程
    % \item Lead engineer in High-Voltage SPICE (Simulation Program with Integrated Circuit Emphasis) team, helped the team to develop several standard operating procedure  (SOP) for experiments, modeling, documenting, guided junior engineers in the team, and provided technique supports to clients.
    \item Lead engineer in the High-Voltage SPICE (Simulation Program with Integrated Circuit Emphasis) team, developed several standard operating procedures (SOP) for experimental measurement, data analysis, model building, and document writing for team members to follow.
    % \item 帶領三個新進部門的同事，手把手教導，使他們快速地熟悉工作環境與工作流程，資料結構，分析手法，並且在需要的時候給予技術指導與幫助 
    \item Supervised three new colleagues in the department and provided hands-on guidance to quickly familiarize them with the work environment, workflow, data architecture, and cutting-dege analysis techniques and high level statistical methods, also provided technical guidance and supports as needed.
\end{itemize}
% \begin{itemize}
%     % \item 把淺在客戶變成付費客戶，藉由提供 preliminary model 符合客戶的要求
%     % \item 把緊急的專案在 deadline 到期之前就做完，然後保留著客戶
%     % \item 和不同的小組與客戶合作，在有限的時間內解決各種存在的 issue
%     % \item 參與300人左右的 RD工程師內部研討會，並且在會後的搶答比賽中獲得第三名
% \end{itemize}

%----------------------------------------------------------------------------------------
%	ACADEMIC SECTION
%----------------------------------------------------------------------------------------

\section{ACADEMIC ACTIVITIES AND PRESENTATIONS}

\begin{itemize}
    \item Electron Isolation Efficiency Measurement - Presented at ATLAS e/gamma workshop 2015, Annecy-le-Vieux, France (2015)
    \item Participant, ATLAS SUSY workshop 2016, Brighton, UK (2016)
    \item  
Electron Isolation Efficiency and Scale Factor Measurement - Invited presentation at ATLAS e/gamma workshop 2016, Thessaloniki Greece, (2016)
    \item Non-Universal Higgs Mass Model with 2 Extra parameters in the Electroweak Interaction with 2 or 3 leptons - Poster session presented at ATLAS Exotics-SUSY Workshop, Bucharest, Romania (2017)
    \item Participant, The 2017 European 
School of High-Energy Physics, Evora, Portugal (2017)
\end{itemize}

%----------------------------------------------------------------------------------------
%	AWARDs SECTION
%----------------------------------------------------------------------------------------

\section{AWARDS}

\begin{itemize}
    \item Won first place in Eve of Nations competition, University of Oklahoma, Norman, OK (2014)
    \item Won Graduate student thesis Awards, The Physical Society of Taiwan (2006)
    \item Won Holistic Achievement Award, Chung Yuan Christian University, Chung Li, Taiwan 1998 - 1999.
    \item Holistic Achievement Award, Chung Yuan Christian University, Chung Li, Taiwan, 1999 - 2000.
    \item Holistic Achievement Award, Chung Yuan Christian University, Chung Li, Taiwan, 2000 - 2001
    \item Academic Achievement Award, Chung Yuan Christian University, Chung Li, Taiwan, 2001 - 2002\\
    Only top 3 students in the graduating class from each college nominated for membership.
\end{itemize}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY SKILLS} 
\textbf{Programming language:} Python, C/C++, Bash shell script, Scala\\
\textbf{Machine learning:} scikit-learn, Apache Spark, Keras, TensorFlow, PyTorch\\
\textbf{Reinforcement learning:} Gym, Stable-Baseline, Ray\\
\textbf{Database:} SQL, Big Query, PostgreSQL, TablePlus, Incorta\\
\textbf{Visualization:} matplotlib, seaborn, bokeh, plotly\\
\textbf{Dashboard:} Google DataStudio, Tableau, Power BI, Dash\\
\textbf{Big Data:} Apache Hadoop, Hive, Cloudera\\
\textbf{Cloud:} Google Cloud Platform, Microsoft Azure, Amazon AWS\\
\textbf{Others:} Git, Jira, Docker\\

%----------------------------------------------------------------------------------------
%	LEADERSHIP SECTION
%---------------------------------------------------------------------------------------- 

\section{LEADERSHIP}

\textbf{President}\hfill{2012-2013, Norman, OK}\\
\textbf{Taiwanese Student Association (TSA) at the University of Oklahoma}\hfill{}
\begin{itemize}
    \item Organized several TSA events in campus to promote Taiwanese culture and cuisine
    \item Organized joint events with the Taiwanese Community in Oklahoma
    \item Led TSA to win the first place of the Eve of Nation at the University of Oklahoma.
\end{itemize}

 

%----------------------------------------------------------------------------------------
% PUBLICATION SECTION
%----------------------------------------------------------------------------------------

\section{PUBLICATIONS}

\textbf{Link to Google Scholar}\\
\url{https://scholar.google.com/citations?hl=en&user=bn6yCS0AAAAJ}\\
\textbf{Link to INSPIRE HEP}\\
\url{https://inspirehep.net/authors/1385815}

\textbf{CERN \& Uinversity of Oklahoma}: 392 publications\\
\textrm{Name on the Publication: }\textbf{Yu-Ting Shen(Oklahoma U.)}\\
\begin{itemize}
    % \item Jet energy scale measurements and their systematic uncertainties in proton-proton collisions at $\sqrt{s}=13$ TeV with the ATLAS detector\\
    % $\diamond$ Published in: Phys.Rev.D 96 (2017) 7, 072002 \\
    % $\diamond$ 880 citations
    % \item Combined measurements of Higgs boson production and decay using up to $80 \textrm{fb}^{-1}$ of proton-proton collision data at $\sqrt{s}=13$ TeV collected with the ATLAS experiment\\
    % $\diamond$ Published in: Phys.Rev.D 101 (2020) 1, 012002\\
    % $\diamond$ 562 citations
    % \item Performance of missing transverse momentum reconstruction with the ATLAS detector using proton-proton collisions at $\sqrt{s}=13$ TeV\\
    % $\diamond$ Published in: Eur.Phys.J.C 78 (2018) 11, 903\\
    % $\diamond$ 552 citations
\item Jet energy scale measurements and their systematic uncertainties in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 96 (2017) 7, 072002\\
$\diamond$ 880 citations
\item Combined measurements of Higgs boson production and decay using up to 80 fb$^{-1}$ of proton-proton collision data at $\sqrt{s} = 13$ TeV collected with the ATLAS experiment\\
$\diamond$ Published in: Phys.Rev.D 101 (2020) 1, 012002\\
$\diamond$ 562 citations
\item Performance of missing transverse momentum reconstruction with the ATLAS detector using proton-proton collisions at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 11, 903\\
$\diamond$ 552 citations
\item Observation of Higgs boson production in association with a top quark pair at the LHC with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 784 (2018) 173-191\\
$\diamond$ 548 citations
\item Electron and photon performance measurements with the ATLAS detector using the 2015–2017 LHC proton-proton collision data\\
$\diamond$ Published in: JINST 14 (2019) 12, P12006\\
$\diamond$ 519 citations
\item ATLAS b-jet identification performance and efficiency measurement with $t\bar{t}$ events in pp collisions at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 11, 970\\
$\diamond$ 487 citations
\item Observation of $H\rightarrow b\bar{b}$ decays and $VH$ production with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 786 (2018) 59-86\\
$\diamond$ 479 citations
\item Search for new high-mass phenomena in the dilepton final state using 36 fb$^{-1}$ of proton-proton collision data at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2017) 182\\
$\diamond$ 449 citations
\item Jet reconstruction and performance using particle flow with the ATLAS Detector\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 7, 466\\
$\diamond$ 437 citations
\item Measurement of the $W$-boson mass in pp collisions at $\sqrt{s} = 7$ TeV\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 2, 110, Eur.Phys.J.C 78 (2018) 11, 898 (erratum)\\
$\diamond$ 411 citations
\item Electron reconstruction and identification in the ATLAS experiment using the 2015 and 2016 LHC proton-proton collision data at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 8, 639\\
$\diamond$ 406 citations
\item Search for dark matter and other new phenomena in events with an energetic jet and large missing transverse momentum using the ATLAS detector\\
$\diamond$ Published in: JHEP 01 (2018) 126\\
$\diamond$ 383 citations
\item Measurements of Higgs boson properties in the diphoton decay channel with 36 fb$^{-1}$ of $pp$ collision data at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 052005\\
$\diamond$ 354 citations
\item Search for high-mass dilepton resonances using 139 fb$^{-1}$ of $pp$ collision data collected at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 796 (2019) 68-87\\
$\diamond$ 342 citations
\item Performance of the ATLAS Track Reconstruction Algorithms in Dense Environments in LHC Run 2\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 10, 673\\
$\diamond$ 340 citations
\item Search for new phenomena in dijet events using 37 fb$^{-1}$ $pp$ collision data collected at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 96 (2017) 5, 052004\\
$\diamond$ 338 citations
\item Performance of electron and photon triggers in ATLAS during LHC Run 2\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 1, 47\\
$\diamond$ 330 citations
\item Search for additional heavy neutral Higgs and gauge bosons in the ditau final state produced in 36 fb$^{-1}$ of $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 01 (2018) 055\\
$\diamond$ 310 citations
\item Measurements of b-jet tagging efficiency with the ATLAS detector using $t\bar{t}$ events at $\sqrt{s} = 13$\\
$\diamond$ Published in: JHEP 08 (2018) 089\\
$\diamond$ 303 citations
\item ATLAS data quality operations and performance for 2015–2018 data-taking\\
$\diamond$ Published in: JINST 15 (2020) 04, P04003\\
$\diamond$ 295 citations
\item Evidence for light-by-light scattering in heavy-ion collisions with the ATLAS detector at the LHC\\
$\diamond$ Published in: Nature Phys. 13 (2017) 9, 852-858\\
$\diamond$ 293 citations
\item Jet energy scale and resolution measured in proton–proton collisions at $\sqrt{s} = 13$ with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 8, 689\\
$\diamond$ 281 citations
\item Performance of the ATLAS muon triggers in Run 2\\
$\diamond$ Published in: JINST 15 (2020) 09, P09015\\
$\diamond$ 267 citations
\item Evidence for the $H \rightarrow b\bar{b}$ decay with the ATLAS detector\\
$\diamond$ Published in: JHEP 12 (2017) 024\\
$\diamond$ 259 citations
\item Search for squarks and gluinos in final states with jets and missing transverse momentum using 36 fb$^{-1}$ of $\sqrt{s} = 13$ TeV pp collision data with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 97 (2018) 11, 112001\\
$\diamond$ 254 citations
\item Search for electroweak production of charginos and sleptons decaying into final states with two leptons and missing transverse momentum in $\sqrt{s} = 13$ TeV $pp$ collisions using the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 2, 123\\
$\diamond$ 251 citations
\item Muon reconstruction and identification efficiency in ATLAS using the full Run 2 $pp$ collision data set at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 7, 578\\
$\diamond$ 249 citations
\item Electron and photon energy calibration with the ATLAS detector using 2015–2016 LHC proton-proton collision data\\
$\diamond$ Published in: JINST 14 (2019) 03, P03017\\
$\diamond$ 225 citations
\item Search for electroweak production of supersymmetric particles in final states with two or three leptons at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 12, 995\\
$\diamond$ 225 citations
\item Cross-section measurements of the Higgs boson decaying into a pair of $\tau$ leptons in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 99 (2019) 072001\\
$\diamond$ 223 citations
\item Search for the standard model Higgs boson produced in association with top quarks and decaying into a $b\bar{b}$ pair in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 97 (2018) 7, 072016\\
$\diamond$ 220 citations
\item Combination of the searches for pair-produced vector-like partners of the third-generation quarks at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.Lett. 121 (2018) 21, 211801\\
$\diamond$ 213 citations
\item Combination of searches for Higgs boson pairs in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 800 (2020) 135103\\
$\diamond$ 212 citations
\item Measurement of the Higgs boson mass in the $H \rightarrow ZZ^{*} \rightarrow 4\ell$ and $H \rightarrow \gamma\gamma$ channels with $\sqrt{s} = 13$ TeV $pp$ collisions using the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 784 (2018) 345-366\\
$\diamond$ 211 citations
\item Search for heavy Higgs bosons decaying into two tau leptons with the ATLAS detector using $pp$ collisions at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Phys.Rev.Lett. 125 (2020) 5, 051801\\
$\diamond$ 211 citations
\item Search for new phenomena in high-mass diphoton final states using 37 fb$^{-1}$ of proton--proton collisions collected at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 775 (2017) 105-125\\
$\diamond$ 210 citations
\item Search for pair production of Higgs bosons in the $b\bar{b}b\bar{b}$ final state using proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 01 (2019) 030\\
$\diamond$ 209 citations
\item Evidence for the associated production of the Higgs boson and a top quark pair with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 97 (2018) 7, 072003\\
$\diamond$ 206 citations
\item Study of the rare decays of $B^{s}_{0}$ and $B^{0}$ mesons into muon pairs using data collected during 2015 and 2016 with the ATLAS detector\\
$\diamond$ Published in: JHEP 04 (2019) 098\\
$\diamond$ 204 citations
\item Measurement of the Higgs boson coupling properties in the $H \rightarrow ZZ^{*} \rightarrow 4\ell$ decay channel at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 03 (2018) 095\\
$\diamond$ 202 citations
\item Angular analysis of $B^{0}_{d} \rightarrow K^{*} \mu^{+}\mu^{-}$ decays in $pp$ collisions at $\sqrt{s} = 8$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2018) 047\\
$\diamond$ 201 citations
\item Search for long-lived charginos based on a disappearing-track signature in pp collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 06 (2018) 022\\
$\diamond$ 197 citations
\item Search for doubly charged Higgs boson production in multi-lepton final states with the ATLAS detector using proton–proton collisions at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 3, 199\\
$\diamond$ 189 citations
\item Search for long-lived, massive particles in events with displaced vertices and missing transverse momentum in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 97 (2018) 5, 052012\\
$\diamond$ 189 citations
\item Search for a scalar partner of the top quark in the jets plus missing transverse momentum final state at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 12 (2017) 085\\
$\diamond$ 186 citations
\item Combination of searches for invisible Higgs boson decays with the ATLAS experiment\\
$\diamond$ Published in: Phys.Rev.Lett. 122 (2019) 23, 231801\\
$\diamond$ 184 citations
\item Search for top-squark pair production in final states with one lepton, jets, and missing transverse momentum using 36 fb$^{-1}$ of $\sqrt{s} = 13$ TeV $pp$ collision data with the ATLAS detector
$\diamond$ Published in: JHEP 06 (2018) 108
$\diamond$ 183 citations
\item Searches for electroweak production of supersymmetric particles with compressed mass spectra in $\sqrt{s} = 13$ TeV $pp$ collision data with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 101 (2020) 5, 052005\\
$\diamond$ 180 citations
\item Measurement of the photon identification efficiencies with the ATLAS detector using LHC Run 2 data collected in 2015 and 2016\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 3, 205\\
$\diamond$ 179 citations
\item Search for charged Higgs bosons decaying via $H^{\pm} \rightarrow \tau^{\pm}\nu_{\tau}$ in the $\tau$+jets and $\tau$+lepton final states with 36 fb$^{-1}$ of $pp$ collision data recorded at $\sqrt{s} = 13$ TeV with the ATLAS experiment\\
$\diamond$ Published in: JHEP 09 (2018) 139
$\diamond$ 178 citations
\item Measurement of the photon identification efficiencies with the ATLAS detector using LHC Run 2 data collected in 2015 and 2016\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 3, 205\\
$\diamond$ 179 citations
\item Search for charged Higgs bosons decaying via $H^{\pm} \rightarrow \tau^{\pm}\nu_{\tau}$ in the $\tau$+jets and $\tau$+lepton final states with 36 fb$^{-1}$ of $pp$ collision data recorded at $\sqrt{s} = 13$ TeV with the ATLAS experiment\\
$\diamond$ Published in: JHEP 09 (2018) 139\\
$\diamond$ 178 citations
\item A search for the dimuon decay of the Standard Model Higgs boson with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 812 (2021) 135980\\
$\diamond$ 177 citations
\item Measurement of the nuclear modification factor for inclusive jets in Pb+Pb collisions at $sqrt(s_{NN}) = 5.02$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 790 (2019) 108-128\\
$\diamond$ 176 citations
\item Measurement of the near-threshold e+ e- ---> D(*)+- D(*)-+ cross section using initial-state radiation\\
$\diamond$ Published in: Phys.Rev.Lett. 98 (2007) 092001\\
$\diamond$ 175 citations
\item Search for electroweak production of supersymmetric states in scenarios with compressed mass spectra at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 97 (2018) 5, 052010\\
$\diamond$ 171 citations
\item Search for heavy resonances decaying into a $W$ or $Z$ boson and a Higgs boson in final states with leptons and $b$-jets in 36 fb$^{-1}$ of $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: JHEP 03 (2018) 174, JHEP 11 (2018) 051 (erratum)\\
$\diamond$ 165 citations
\item Search for heavy resonances decaying into $WW$ in the $e\nu\mu\nu$ final state in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 1, 24\\
$\diamond$ 163 citations
\item Search for dark matter at $\sqrt{s} = 13$ TeV in final states containing an energetic photon and large missing transverse momentum with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 6, 393\\
$\diamond$ 161 citations
\item Search for new resonances in mass distributions of jet pairs using 139 fb$^{-1}$ of $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 03 (2020) 145\\
$\diamond$ 156 citations
\item Measurement of the $t\bar{t}Z$ and $t\bar{t}W$ cross sections in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 99 (2019) 7, 072009\\
$\diamond$ 156 citations
\item Measurements of gluon-gluon fusion and vector-boson fusion Higgs boson production cross-sections in the $H \rightarrow WW^{*} \rightarrow e\nu\mu\nu$ decay channel in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 789 (2019) 508-529\\
$\diamond$ 155 citations
\item Search for heavy neutral leptons in decays of $W$ bosons produced in 13 TeV $pp$ collisions using prompt and displaced signatures with the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2019) 265\\
$\diamond$ 154 citations
\item Search for an invisibly decaying Higgs boson or dark matter candidates produced in association with a $Z$ boson in $pp$ collisions at $\sqrt{s} = 13$ with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 776 (2018) 318-337\\
$\diamond$ 154 citations
\item Search for heavy ZZ resonances in the $\ell^{+}\ell^{-}\ell^{+}\ell^{-}$ and $\ell^{+}\ell^{-}\nu\bar{nu}$ final states using proton–proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 4, 293\\
$\diamond$ 147 citations
\item Search for charged Higgs bosons decaying into top and bottom quarks at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 11 (2018) 085\\
$\diamond$ 146 citations
\item Search for resonant and non-resonant Higgs boson pair production in the $b\bar{b}\tau^{+}\tau^{-}$ decay channel in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.Lett. 121 (2018) 19, 191801, Phys.Rev.Lett. 122 (2019) 8, 089901 (erratum)\\
$\diamond$ 145 citations
\item Search for Higgs boson pair production in the $\gamma \gamma b\bar{b}$ final state with 13 TeV $pp$ collision data collected by the ATLAS experiment\\
$\diamond$ Published in: JHEP 11 (2018) 040\\
$\diamond$ 144 citations
\item Constraints on mediator-based dark matter and scalar dark energy models using $\sqrt{s} = 13$ TeV $pp$ collision data collected by the ATLAS detector\\
$\diamond$ Published in: JHEP 05 (2019) 142\\
$\diamond$ 143 citations
\item Observation of light-by-light scattering in ultraperipheral Pb+Pb collisions with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.Lett. 123 (2019) 5, 052001\\
$\diamond$ 141 citations
\item Search for heavy particles decaying into top-quark pairs using lepton-plus-jets events in proton–proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 7, 565\\
$\diamond$ 141 citations
\item Experimental constraints on the possible J**P quantum numbers of the Lambda(c)(2880)+\\
$\diamond$ Published in: Phys.Rev.Lett. 98 (2007) 262001\\
$\diamond$ 137 citations
\item Search for low-mass dijet resonances using trigger-level jets with the ATLAS detector in $pp$ collisions at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Phys.Rev.Lett. 121 (2018) 8, 081801\\
$\diamond$ 136 citations
\item Search for new phenomena in events with same-charge leptons and $b$-jets in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 12 (2018) 039\\
$\diamond$ 134 citations
\item Search for new phenomena in events with an energetic jet and missing transverse momentum in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 103 (2021) 11, 112006\\
$\diamond$ 133 citations
\item Measurement of the top quark mass in the $t\bar{t} \rightarrow$ lepton+jets channel from $\sqrt{s} = 8$ TeV ATLAS data and combination with previous results\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 4, 290\\
$\diamond$ 131 citations
\item Combination of searches for heavy resonances decaying into bosonic and leptonic final states using 36 fb$^{-1}$ of proton-proton collision data at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 5, 052008\\
$\diamond$ 131 citations
\item Search for supersymmetry in final states with two same-sign or three leptons and jets using 36 fb$^{-1}$ of $\sqrt{s} = 13$ TeV $pp$ collision data with the ATLAS detector\\
$\diamond$ Published in: JHEP 09 (2017) 084, JHEP 08 (2019) 121 (erratum)\\
$\diamond$ 128 citations
\item Search for heavy charged long-lived particles in the ATLAS detector in 36.1 fb$^{-1}$ of proton-proton collision data at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Phys.Rev.D 99 (2019) 9, 092007\\
$\diamond$ 128 citations
\item Search for the Decay of the Higgs Boson to Charm Quarks with the ATLAS Experiment\\
$\diamond$ Published in: Phys.Rev.Lett. 120 (2018) 21, 211802\\
$\diamond$ 127 citations
\item Measurements of $WH$ and $ZH$ production in the $H \rightarrow b\bar{b}$ decay channel in $pp$ collisions at 13 TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 2, 178\\
$\diamond$ 127 citations
\item Measurement of inclusive and differential cross sections in the $H \rightarrow ZZ^{*} \rightarrow 4\ell$ decay channel in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2017) 132\\
$\diamond$ 127 citations
\item Higgs boson production cross-section measurements and their EFT interpretation in the $4\ell$ decay channel at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 10, 957, Eur.Phys.J.C 81 (2021) 1, 29 (erratum), Eur.Phys.J.C 81 (2021) 5, 398 (erratum)\\
$\diamond$ 126 citations
\item Search for $WW/WZ$ resonance production in $\ell \nu qq$ final states in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 03 (2018) 042\\
$\diamond$ 124 citations
\item Measurement of multi-particle azimuthal correlations in $pp$, $p$+Pb and low-multiplicity Pb+Pb collisions with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 6, 428\\
$\diamond$ 124 citations
\item Constraints on off-shell Higgs boson production and the Higgs boson total width in $ZZ \rightarrow 4\ell$ and $ZZ \rightarrow 2\ell 2\nu$ final states with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 786 (2018) 223-244\\
$\diamond$ 123 citations
\item Search for Heavy Higgs Bosons $A/H$ Decaying to a Top Quark Pair in $pp$ collisions at $\sqrt{s} = 8$ TeV with the ATLAS Detector\\
$\diamond$ Published in: Phys.Rev.Lett. 119 (2017) 19, 191803\\
$\diamond$ 122 citations
\item Search for dark matter produced in association with bottom or top quarks in $\sqrt{s} = 13$ TeV pp collisions with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 1, 18\\
$\diamond$ 122 citations
\item Performance of top-quark and $W$-boson tagging with ATLAS in Run 2 of the LHC\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 5, 375\\
$\diamond$ 118 citations
\item Search for pair production of heavy vector-like quarks decaying to high-p$_{T}$ W bosons and b quarks in the lepton-plus-jets final state in pp collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2017) 141\\
$\diamond$ 116 citations
\item Identification and rejection of pile-up jets at high pseudorapidity with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 9, 580, Eur.Phys.J.C 77 (2017) 10, 712 (erratum)\\
$\diamond$ 115 citations
\item Searches for heavy $ZZ$ and $ZW$ resonances in the $\ell\ell qq$ and $\nu\nu qq$ final states in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 03 (2018) 009\\
$\diamond$ 115 citations
\item Search for Dark Matter Produced in Association with a Higgs Boson Decaying to $b\bar{b}$ using 36 fb$^{-1}$ of $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS Detector\\
$\diamond$ Published in: Phys.Rev.Lett. 119 (2017) 18, 181804\\
$\diamond$ 114 citations
\item Operation of the ATLAS trigger system in Run 2\\
$\diamond$ Published in: JINST 15 (2020) 10, P10004\\
$\diamond$ 114 citations
\item In situ calibration of large-radius jet energy and mass in 13 TeV proton–proton collisions with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 2, 135\\
$\diamond$ 114 citations
\item Measurement of quarkonium production in proton–lead and proton–proton collisions at 5.02 TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 3, 171\\
$\diamond$ 114 citations
\item Measurement of $W^{\pm}Z$ production cross sections and gauge boson polarisation in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 6, 535\\
$\diamond$ 113 citations
\item Searches for third-generation scalar leptoquarks in $\sqrt{s} = 13$ $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: JHEP 06 (2019) 144\\
$\diamond$ 112 citations
\item Observation of electroweak production of a same-sign $W$ boson pair in association with two jets in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.Lett. 123 (2019) 16, 161801\\
$\diamond$ 111 citations
\item Search for the dimuon decay of the Higgs boson in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.Lett. 119 (2017) 5, 051802\\
$\diamond$ 111 citations
\item Search for the dimuon decay of the Higgs boson in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.Lett. 119 (2017) 5, 051802\\
$\diamond$ 111 citations
\item Search for a heavy charged boson in events with a charged lepton and missing transverse momentum from $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 100 (2019) 5, 052013\\
$\diamond$ 111 citations
\item Measurement of long-range multiparticle azimuthal correlations with the subevent cumulant method in $pp$ and $p$+Pbcollisions with the ATLAS detector at the CERN Large Hadron Collider\\
$\diamond$ Published in: Phys.Rev.C 97 (2018) 2, 024904\\
$\diamond$ 111 citations
\item CP Properties of Higgs Boson Interactions with Top Quarks in the $t\bar{t}H$ and $tH$ Processes Using $H \rightarrow \gamma \gamma$ with the ATLAS Detector\\
$\diamond$ Published in: Phys.Rev.Lett. 125 (2020) 6, 061802\\
$\diamond$ 110 citations
\item Prompt and non-prompt $J/\psi$ and $\psi(2S)$ suppression at high transverse momentum in 5.02 TeV Pb+Pb collisions with the ATLAS experiment\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 9, 762\\
$\diamond$ 109 citations
\item Search for pair production of up-type vector-like quarks and for four-top-quark events in final states with multiple $b$-jets with the ATLAS detector\\
$\diamond$ Published in: JHEP 07 (2018) 089\\
$\diamond$ 108 citations
\item Search for dark matter in events with a hadronically decaying vector boson and missing transverse momentum in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2018) 180\\
$\diamond$ 108 citations
\item Measurements of $t\bar{t}$ differential cross-sections of highly boosted top quarks decaying to all-hadronic final states in $pp$ collisions at $\sqrt{s} = 13$ TeV using the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 1, 012003\\
$\diamond$ 107 citations
\item Search for chargino-neutralino production using recursive jigsaw reconstruction in final states with two or three charged leptons in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 9, 092012\\
$\diamond$ 107 citations
\item Search for pair production of vector-like top quarks in events with one lepton, jets, and missing transverse momentum in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: JHEP 08 (2017) 052\\
$\diamond$ 107 citations
\item Search for direct top squark pair production in final states with two leptons in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 12, 898\\
$\diamond$ 106 citations
\item Measurement of the Soft-Drop Jet Mass in pp Collisions at $\sqrt{s} = 13$ TeV with the ATLAS Detector\\
$\diamond$ Published in: Phys.Rev.Lett. 121 (2018) 9, 092001\\
$\diamond$ 106 citations
\item Search for pairs of scalar leptoquarks decaying into quarks and electrons or muons in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2020) 112\\
$\diamond$ 104 citations
\item Search for light resonances decaying to boosted quark pairs and produced in association with a photon or a jet in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 788 (2019) 316-335\\
$\diamond$ 103 citations
\item Search for Higgs boson decays to beyond-the-Standard-Model light bosons in four-lepton events with the ATLAS detector at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: JHEP 06 (2018) 166\\
$\diamond$ 103 citations
\item Searches for the $Z \gamma$ decay mode of the Higgs boson and for new high-mass resonances in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2017) 112\\
$\diamond$ 103 citations
\item Search for a scalar partner of the top quark in the all-hadronic $t\bar{t}$ plus missing transverse momentum final state at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 8, 737\\
$\diamond$ 103 citations
\item Measurement of the $t\bar{t}$ production cross-section and lepton differential distributions in $e\mu$ dilepton events from $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 6, 528\\
$\diamond$ 101 citations
\item Search for a heavy Higgs boson decaying into a $Z$ boson and another heavy Higgs boson in the $\ell \ell bb$ final state in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 783 (2018) 392-414\\
$\diamond$ 101 citations
\item Measurement of the cross section for inclusive isolated-photon production in $pp$ collisions at $\sqrt{s} = 13$ TeV using the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 770 (2017) 473-493\\
$\diamond$ 101 citations
\item Search for a new heavy gauge boson resonance decaying into a lepton and missing transverse momentum in 36 fb$^{-1}$ of $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS experiment\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 5, 401\\
$\diamond$ 100 citations
\item A search for pair-produced resonances in four-jet final states at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 3, 250\\
$\diamond$ 100 citations
\item $ZZ \rightarrow \ell^{+}\ell^{-}\ell'^{+}\ell'^{-}$ cross-section measurements and search for anomalous triple gauge couplings in 13 TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 97 (2018) 3, 032005\\
$\diamond$ 99 citations
\item Search for diboson resonances with boson-tagged jets in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 777 (2018) 91-113\\
$\diamond$ 99 citations
\item Measurement of inclusive jet and dijet cross-sections in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 05 (2018) 195\\
$\diamond$ 98 citations
\item Search for pair- and single-production of vector-like quarks in final states with at least one $Z$ boson decaying into a pair of electrons or muons in $pp$collision data collected with the ATLAS detector at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 11, 112010\\
$\diamond$ 94 citations
\item Search for invisible Higgs boson decays in vector boson fusion at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 793 (2019) 499-519\\
$\diamond$ 94 citations
\item Search for long-lived particles produced in $pp$ collisions at $\sqrt{s} = 13$ TeV that decay into displaced hadronic jets in the ATLAS muon spectrometer\\
$\diamond$ Published in: Phys.Rev.D 99 (2019) 5, 052005\\
$\diamond$ 93 citations
\item Search for heavy Majorana or Dirac neutrinos and right-handed $W$ gauge bosons in final states with two charged leptons and two jets at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 01 (2019) 016\\
$\diamond$ 92 citations
\item Search for the Higgs boson produced in association with a vector boson and decaying into two spin-zero particles in the $H \rightarrow aa \rightarrow 4b$ channel in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2018) 031\\
$\diamond$ 92 citations
\item Study of the material of the ATLAS inner detector for Run 2 of the LHC\\
$\diamond$ Published in: JINST 12 (2017) 12, P12009\\
$\diamond$ 91 citations
\item Measurements of the Higgs boson inclusive and differential fiducial cross sections in the $4\ell$ decay channel at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 10, 942\\
$\diamond$ 90 citations
\item Measurement of longitudinal flow decorrelations in Pb+Pb collisions at $\sqrt{s_{NN}} = 2.76$ and 5.02 TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 2, 142\\
$\diamond$ 90 citations
\item Search for long-lived neutral particles in $pp$ collisions at $\sqrt{s} = 13$ TeV that decay into displaced hadronic jets in the ATLAS calorimeter\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 6, 481\\
$\diamond$ 89 citations
\item Observation of electroweak $W^{\pm}Z$ boson pair production in association with two jets in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 793 (2019) 469-492\\
$\diamond$ 88 citations
\item Search for supersymmetry in final states with missing transverse momentum and multiple $b$-jets in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 06 (2018) 107\\
$\diamond$ 88 citations
\item Measurement of jet fragmentation in Pb+Pb and $pp$ collisions at $\sqrt{s_{NN}} = 5.02$ TeV with the ATLAS detector
$\diamond$ Published in: Phys.Rev.C 98 (2018) 2, 024908\\
$\diamond$ 88 citations
\item Search for Higgs boson pair production in the $\gamma\gamma WW^{*}$ channel using $pp$collision data recorded at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 12, 1007\\
$\diamond$ 87 citations
\item Measurements of top-quark pair differential cross-sections in the lepton+jets channel in $pp$ collisions at $\sqrt{s} = 13$ TeV using the ATLAS detector\\
$\diamond$ Published in: JHEP 11 (2017) 191\\
$\diamond$ 86 citations
\item Search for heavy resonances decaying into a pair of $Z$ bosons in the $\ell^{+}\ell^{-}\ell'^{+}\ell'^{-}$ and $\ell^{+}\ell^{-}\nu\bar{nu}$  final states using 139 fb$^{-1}$ of proton–proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 4, 332\\
$\diamond$ 86 citations
\item Search for doubly charged scalar bosons decaying into same-sign $W$ boson pairs with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 1, 58\\
$\diamond$ 85 citations
\item Search for heavy diboson resonances in semileptonic final states in pp collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 12, 1165\\
$\diamond$ 84 citations
\item Measurements of inclusive and differential fiducial cross-sections of $t\bar{t}$ production with additional heavy-flavour jets in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 04 (2019) 046\\
$\diamond$ 84 citations
\item Measurement of the top-quark mass in $t\bar{t} + 1$-jet events collected with the ATLAS detector in $pp$ collisions at $\sqrt{s} = 8$ TeV\\
$\diamond$ Published in: JHEP 11 (2019) 150\\
$\diamond$ 84 citations
\item Search for Higgs boson pair production in the $b\bar{b}WW{*}$ decay mode at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 04 (2019) 092\\
$\diamond$ 84 citations
\item Search for supersymmetry in events with $b$-tagged jets and missing transverse momentum in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 11 (2017) 195\\
$\diamond$ 84 citations
\item Search for the $HH \rightarrow b\bar{b}b\bar{b}$ process via vector-boson fusion production using proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 07 (2020) 108, JHEP 01 (2021) 145 (erratum), JHEP 05 (2021) 207 (erratum)\\
$\diamond$ 84 citations
\item Measurement of fiducial and differential $W^{+}W^{-}$ production cross-sections at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 10, 884\\
$\diamond$ 84 citations
\item Measurement of the production cross-section of a single top quark in association with a Z boson in proton–proton collisions at 13 TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 780 (2018) 557-577\\
$\diamond$ 84 citations
\item Measurement of the azimuthal anisotropy of charged particles produced in $\sqrt{s_{NN}} = 5.02$ TeV Pb+Pb collisions with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 12, 997\\
$\diamond$ 4 citations
\item Search for top quark decays $t \rightarrow qH$, with $H \rightarrow \gamma\gamma$ in $\sqrt{s} = 13$ TeV $pp$ collisions using the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2017) 129\\
$\diamond$ 83 citations
\item Measurement of the Drell-Yan triple-differential cross section in $pp$ collisions at $\sqrt{s} = 8$ TeV\\
$\diamond$ Published in: JHEP 12 (2017) 059\\
$\diamond$ 83 citations
\item Search for squarks and gluinos in final states with jets and missing transverse momentum using 139 fb$^{-1}$ of $\sqrt{s} = 13$ TeV $pp$collision data with the ATLAS detector\\
$\diamond$ Published in: JHEP 02 (2021) 143\\
$\diamond$ 82 citations
\item Dijet resonance search with weak supervision using $\sqrt{s} = 13$ TeV $pp$ collisions in the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.Lett. 125 (2020) 13, 131801\\
$\diamond$ 82 citations
\item Observation of centrality-dependent acoplanarity for muon pairs produced via two-photon scattering in Pb+Pb collisions at $\sqrt{s_{NN}} = 5.02$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.Lett. 121 (2018) 21, 212301\\
$\diamond$ 80 citations
\item Search for heavy resonances decaying to a $W$ or $Z$ boson and a Higgs boson in the $q\bar{q}^{(')}b\bar{b}$ final state in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 774 (2017) 494-515\\
$\diamond$ 80 citations
\item Search for supersymmetry in events with four or more leptons in $\sqrt{s} = 13$ TeV $pp$ collisions with ATLAS\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 3, 032009\\
$\diamond$ 79 citations
\item Measurement of lepton differential distributions and the top quark mass in $t\bar{t}$ production in $pp$ collisions at $\sqrt{s} = 8$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 11, 804\\
$\diamond$ 78 citations
\item Search for direct production of electroweakinos in final states with one lepton, missing transverse momentum and a Higgs boson decaying into two $b$-jets in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 8, 691\\
$\diamond$ 78 citations
\item Combined measurement of differential and total cross sections in the $H \rightarrow \gamma \gamma$ and the $H \rightarrow ZZ \rightarrow 4\ell$ decay channels at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 786 (2018) 114-133\\
$\diamond$ 78 citations
\item Search for pair production of heavy vector-like quarks decaying into hadronic final states in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 9, 092005\\
$\diamond$ 78 citations
\item Search for four-top-quark production in the single-lepton and opposite-sign dilepton final states in pp collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 99 (2019) 5, 052009\\
$\diamond$ 77 citations
\item Search for chargino-neutralino production with mass splittings near the electroweak scale in three-lepton final states in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 101 (2020) 7, 072001\\
$\diamond$ 77 citations
\item Search for flavour-changing neutral current top-quark decays $t \rightarrow qZ$ in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 07 (2018) 176\\
$\diamond$ 76 citations
\item Search for dark matter in association with a Higgs boson decaying to two photons at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 96 (2017) 11, 112004\\
$\diamond$ 76 citations
\item Search for the direct production of charginos and neutralinos in final states with tau leptons in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 2, 154\\
$\diamond$ 76 citations
\item Measurement of soft-drop jet observables in $pp$ collisions with the ATLAS detector at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Phys.Rev.D 101 (2020) 5, 052007\\
$\diamond$ 75 citations
\item Search for the Higgs boson decays $H \rightarrow ee$ and $H \rightarrow e\mu$ in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 801 (2020) 135148\\
$\diamond$ 75 citations
\item Measurement of light-by-light scattering and search for axion-like particles with 2.2 nb$^{-1}$ of Pb+Pb data with the ATLAS detector\\
$\diamond$ Published in: JHEP 11 (2021) 050 (erratum), JHEP 03 (2021) 243\\
$\diamond$ 75 citations
\item Search for pair production of heavy vector-like quarks decaying into high-$p_{T}$ $W$ bosons and top quarks in the lepton-plus-jets final state in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 08 (2018) 048\\
$\diamond$ 75 citations
\item Search for direct stau production in events with two hadronic $\tau$-leptons in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 101 (2020) 3, 032009\\
$\diamond$ 74 citations
\item Performance of the ATLAS Transition Radiation Tracker in Run 1 of the LHC: tracker properties\\
$\diamond$ Published in: JINST 12 (2017) 05, P05002\\
$\diamond$ 74 citations
\item Search for Higgs bosons produced via vector-boson fusion and decaying into bottom quark pairs in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 5, 052003\\
$\diamond$ 73 citations
\item Search for long-lived particles in final states with displaced dimuon vertices in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 99 (2019) 1, 012001\\
$\diamond$ 73 citations
\item Measurement of the exclusive $\gamma \gamma \rightarrow \mu^{+} \mu^{-}$ process in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 777 (2018) 303-323\\
$\diamond$ 72 citations
\item Search for diboson resonances in hadronic final states in 139 fb$^{-1}$ of $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 09 (2019) 091, JHEP 06 (2020) 042 (erratum)\\
$\diamond$ 72 citations
\item A search for the $Z\gamma$ decay mode of the Higgs boson in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 809 (2020) 135754\\
$\diamond$ 71 citations
\item Search for Higgs boson pair production in the $WW^{(*)}WW^{(*)}$ decay channel using ATLAS data recorded at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: JHEP 05 (2019) 124\\
$\diamond$ 71 citations
\item Measurement of photon–jet transverse momentum correlations in 5.02 TeV Pb + Pb and $pp$ collisions with ATLAS\\
$\diamond$ Published in: Phys.Lett.B 789 (2019) 167-190\\
$\diamond$ 71 citations
\item Search for low-mass resonances decaying into two jets and produced in association with a photon using $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 795 (2019) 56-75\\
$\diamond$ 71 citations
\item Search for High-Mass Resonances Decaying to $\tau\nu$ in pp Collisions at $\sqrt{s} = 13$ TeV with the ATLAS Detector\\
$\diamond$ Published in: Phys.Rev.Lett. 120 (2018) 16, 161802\\
$\diamond$ 70 citations
\item Search for chargino and neutralino production in final states with a Higgs boson and missing transverse momentum at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 100 (2019) 1, 012006\\
$\diamond$ 70 citations
\item Studies of $Z\gamma$ production in association with a high-mass dijet system in $pp$ collisions at $\sqrt{s} = 8$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 07 (2017) 107\\
$\diamond$ 70 citations
\item Measurements of inclusive and differential fiducial cross-sections of $t\bar{t}\gamma$ production in leptonic final states at $\sqrt{s} = 13$ in ATLAS\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 5, 382\\
$\diamond$ 69 citations
\item Search for squarks and gluinos in events with an isolated lepton, jets, and missing transverse momentum at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 96 (2017) 11, 112010\\
$\diamond$ 69 citations
\item Searches for lepton-flavour-violating decays of the Higgs boson in $\sqrt{s} = 13$ TeV pp collisions with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 800 (2020) 135069\\
$\diamond$ 69 citations
\item Search for top-quark decays $t \rightarrow Hq$ with 36 fb$^{-1}$ of $pp$collision data at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 05 (2019) 123\\
$\diamond$ 68 citations
\item Measurement of the transverse momentum distribution of Drell–Yan lepton pairs in proton–proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 7, 616\\
$\diamond$ 68 citations
\item Search for single production of vector-like quarks decaying into $Wb$ in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 05 (2019) 164\\
$\diamond$ 68 citations
\item Performance of the missing transverse momentum triggers for the ATLAS detector during Run-2 data taking\\
$\diamond$ Published in: JHEP 08 (2020) 080\\
$\diamond$ 68 citations
\item Search for photonic signatures of gauge-mediated supersymmetry in 13 TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 97 (2018) 9, 092006\\
$\diamond$ 67 citations
\item Search for pair production of third-generation scalar leptoquarks decaying into a top quark and a $\tau$-lepton in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 06 (2021) 179\\
$\diamond$ 67 citations
\item Search for Higgs boson decays into a pair of light bosons in the $bb\mu\mu$ final state in $pp$collision at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 790 (2019) 1-21\\
$\diamond$ 67 citations
\item Search for heavy neutral Higgs bosons produced in association with $b$-quarks and decaying into $b$-quarks at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 102 (2020) 3, 032004\\
$\diamond$ 66 citations
\item Search for squarks and gluinos in final states with same-sign leptons and jets using 139 fb$^{-1}$ of data collected with the ATLAS detector\\
$\diamond$ Published in: JHEP 06 (2020) 046\\
$\diamond$ 66 citations
\item Measurement of differential cross sections and $W^{+}/W^{-}$ cross-section ratios for $W$ boson production in association with jets at $\sqrt{s} = 8$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 05 (2018) 077, JHEP 10 (2020) 048 (erratum)\\
$\diamond$ 66 citations
\item Searches for scalar leptoquarks and differential cross-section measurements in dilepton-dijet events in proton-proton collisions at a centre-of-mass energy of $\sqrt{s} = 13$ TeV with the ATLAS experiment\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 9, 733\\
$\diamond$ 66 citations
\item Search for resonances in the mass distribution of jet pairs with one or two jets identified as $b$-jets in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 032016\\
$\diamond$ 66 citations
\item Measurements of top-quark pair spin correlations in the $e\mu$ channel at $\sqrt{s} = 13$ TeV using $pp$ collisions in the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 8, 754\\
$\diamond$ 66 citations
\item Measurement of VH, $H \rightarrow b\bar{b}$ production as a function of the vector-boson transverse momentum in 13 TeV pp collisions with the ATLAS detector\\
$\diamond$ Published in: JHEP 05 (2019) 141 \\
$\diamond$ 66 citations
\item Search for light long-lived neutral particles produced in $pp$ collisions at $\sqrt{s} = 13$ TeV and decaying into collimated leptons or light hadrons with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 5, 450\\
$\diamond$ 66 citations
\item Observation of the associated production of a top quark and a $Z$ boson in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 07 (2020) 124\\
$\diamond$ 66 citations
\item Determination of jet calibration and energy resolution in proton-proton collisions at $\sqrt{s} = 8$ TeV using the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 12, 1104\\
$\diamond$ 65 citations
\item Searches for exclusive Higgs and $Z$ boson decays into $J/\psi\gamma, \psi(2S)\gamma,$ and $\Upsilon(nS)\gamma$ at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 786 (2018) 134-155\\
$\diamond$ 65 citations
\item Search for new phenomena in a lepton plus high jet multiplicity final state with the ATLAS experiment using $\sqrt{s} = 13$ TeV proton-proton collision data\\
$\diamond$ Published in: JHEP 09 (2017) 088\\
$\diamond$ 63 citations
\item Measurement of the associated production of a Higgs boson decaying into $b$-quarks with a vector boson at high transverse momentum in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 816 (2021) 136204\\
$\diamond$ 62 citations
\item Measurement of charged-particle distributions sensitive to the underlying event in $\sqrt{s} = 13$ TeV proton-proton collisions with the ATLAS detector at the LHC\\
$\diamond$ Published in: JHEP 03 (2017) 157\\
$\diamond$ 62 citations
\item Search for heavy particles decaying into a top-quark pair in the fully hadronic final state in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 99 (2019) 9, 092004\\
$\diamond$ 62 citations
\item Measurements of top-quark pair to $Z$-boson cross-section ratios at $\sqrt{s} = 13, 8, 7$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 02 (2017) 117\\
$\diamond$ 61 citations
\item Measurement of the $t\bar{t}$ production cross-section in the lepton+jets channel at $\sqrt{s} = 13$ TeV with the ATLAS experiment\\
$\diamond$ Published in: Phys.Lett.B 810 (2020) 135797\\
$\diamond$ 60 citations
\item Search for doubly and singly charged Higgs bosons decaying into vector bosons in multi-lepton final states with the ATLAS detector using proton-proton collisions at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: JHEP 06 (2021) 146\\
$\diamond$ 60 citations
\item Determination of the strong coupling constant $\alpha_{s}$ from transverse energy–energy correlations in multijet events at $\sqrt{s} = 8$ TeV using the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 12, 872\\
$\diamond$ 60 citations
\item Search for a right-handed gauge boson decaying into a high-momentum heavy neutrino and a charged lepton in $pp$ collisions with the ATLAS detector at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Phys.Lett.B 798 (2019) 134942\\
$\diamond$ 60 citations
\item Comparison of Fragmentation Functions for Jets Dominated by Light Quarks and Gluons from $pp$and Pb+Pb Collisions in ATLAS\\
$\diamond$ Published in: Phys.Rev.Lett. 123 (2019) 4, 042001\\
$\diamond$ 60 citations
\item Test of the universality of $\tau$ and $\mu$ lepton couplings in $W$-boson decays with the ATLAS detector\\
$\diamond$ Published in: Nature Phys. 17 (2021) 7, 813-818\\
$\diamond$ 59 citations
\item Measurement of the $t\bar{t}\gamma$ production cross section in proton-proton collisions at $\sqrt{s} = 8$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 11 (2017) 086\\
$\diamond$ 59 citations
\item Search for non-resonant Higgs boson pair production in the $bb\ell\nu\ell\nu$ final state with the ATLAS detector in $pp$ collisions at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Phys.Lett.B 801 (2020) 135145\\
$\diamond$ 59 citations
\item Measurement of the Lund Jet Plane Using Charged Particles in 13 TeV Proton-Proton Collisions with the ATLAS Detector\\
$\diamond$ Published in: Phys.Rev.Lett. 124 (2020) 22, 222002\\
$\diamond$ 58 citations
\item Search for a Structure in the $B^{0}_{s}\pi^{\pm}$ Invariant Mass Spectrum with the ATLAS Experiment\\
$\diamond$ Published in: Phys.Rev.Lett. 120 (2018) 20, 202007\\
$\diamond$ 57 citations
\item Search for exclusive Higgs and $Z$ boson decays to $\phi\gamma$ and $\rho\gamma$ with the ATLAS detector\\
$\diamond$ Published in: JHEP 07 (2018) 127\\
$\diamond$ 57 citations
\item Search for $W' \rightarrow tb$ decays in the hadronic final state using pp collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 781 (2018) 327-348\\
$\diamond$ 57 citations
\item Measurement of flow harmonics correlations with mean transverse momentum in lead-lead and proton-lead collisions at $\sqrt{s_{NN}} = 5.02$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 12, 985\\
$\diamond$ 55 citations
\item Measurements of electroweak $Wjj$ production and constraints on anomalous gauge couplings with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 7, 474\\
$\diamond$ 55 citations
\item Combinations of single-top-quark production cross-section measurements and $|f_{LV}V_{tb}|$ determinations at $\sqrt{s} = 7$ and 8 TeV with the ATLAS and CMS experiments\\
$\diamond$ Published in: JHEP 05 (2019) 088\\
$\diamond$ 55 citations
\item Search for long-lived neutral particles produced in $pp$ collisions at $\sqrt{s} = 13$ TeV decaying into displaced hadronic jets in the ATLAS inner detector and muon spectrometer\\
$\diamond$ Published in: Phys.Rev.D 101 (2020) 5, 052013\\
$\diamond$ 55 citations
\item Measurements of integrated and differential cross sections for isolated photon pair production in $pp$ collisions at $\sqrt{s} = 8$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 95 (2017) 11, 112005\\
$\diamond$ 55 citations
\item Search for resonant $WZ$ production in the fully leptonic final state in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 787 (2018) 68-88\\
$\diamond$ 54 citations
\item Search for long-lived, massive particles in events with a displaced vertex and a muon with large impact parameter in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 102 (2020) 3, 032006\\
$\diamond$ 54 citations
\item Search for Magnetic Monopoles and Stable High-Electric-Charge Objects in 13 Tev Proton-Proton Collisions with the ATLAS Detector\\
$\diamond$ Published in: Phys.Rev.Lett. 124 (2020) 3, 031802\\
$\diamond$ 54 citations
\item Identification of boosted Higgs bosons decaying into $b$-quark pairs with the ATLAS detector at 13 TeV\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 10, 836\\
$\diamond$ 54 citations
\item Search for supersymmetry in final states with charm jets and missing transverse momentum in 13 TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: JHEP 09 (2018) 050\\
$\diamond$ 54 citations
\item Search for new non-resonant phenomena in high-mass dilepton final states with the ATLAS detector\\
$\diamond$ Published in: JHEP 11 (2020) 005, JHEP 04 (2021) 142 (erratum)\\
$\diamond$ 54 citations
\item Measurement of the cross section for isolated-photon plus jet production in $pp$ collisions at $\sqrt{s} = 13$ TeV using the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 780 (2018) 578-602\\
$\diamond$ 53 citations
\item Search for displaced vertices of oppositely charged leptons from decays of long-lived particles in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 801 (2020) 135114\\
$\diamond$ 53 citations
\item Test of CP invariance in vector-boson fusion production of the Higgs boson in the $H \rightarrow \tau\tau$ channel in proton–proton collisions at s=13TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 805 (2020) 135426\\
$\diamond$ 53 citations
\item Search for pair production of higgsinos in final states with at least three $b$-tagged jets in $\sqrt{s} = 13$ TeV $pp$ collisions using the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 9, 092002\\
$\diamond$ 53 citations
\item Search for Higgs boson decays into pairs of light (pseudo)scalar particles in the $\gamma\gamma jj$ final state in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 782 (2018) 750-767\\
$\diamond$ 52 citations
\item Search for new phenomena in events with two opposite-charge leptons, jets and missing transverse momentum in pp collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 04 (2021) 165\\
$\diamond$ 52 citations
\item Search for new phenomena in final states with $b$-jets and missing transverse momentum in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: JHEP 05 (2021) 093\\
$\diamond$ 51 citations
\item Measurement of the production cross section for a Higgs boson in association with a vector boson in the $H \rightarrow WW^{*} \rightarrow \ell\nu\ell\nu$ channel in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 798 (2019) 134949\\
$\diamond$ 51 citations
\item Measurements of $W$ and $Z$ boson production in $pp$ collisions at $\sqrt{s} = 5.02$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 2, 128, Eur.Phys.J.C 79 (2019) 5, 374 (erratum)\\
$\diamond$ 51 citations
\item Search for new phenomena with top quark pairs in final states with one lepton, jets, and missing transverse momentum in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 04 (2021) 174\\
$\diamond$ 50 citations
\item Search for bottom-squark pair production with the ATLAS detector in final states containing Higgs bosons, $b$-jets and missing transverse momentum\\
$\diamond$ Published in: JHEP 12 (2019) 060\\
$\diamond$ 50 citations
\item Measurement of jet $p_{T}$ correlations in Pb+Pb and $pp$ collisions at $\sqrt{s_{NN}} = 2.76$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 774 (2017) 379-402\\
$\diamond$ 50 citations
\item Search for flavor-changing neutral currents in top quark decays $t \rightarrow Hc$ and $t \rightarrow Hu$ in multilepton final states in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 3, 032002\\
$\diamond$ 50 citations
\item Search for $t\bar{t}$ resonances in fully hadronic final states in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2020) 061\\
$\diamond$ 50 citations
\item Measurement of the $CP$-violating phase $\phi_{s}$ in $B^{0}_{s} \rightarrow J/\psi\phi$ decays in ATLAS at 13 TeV\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 4, 342\\
$\diamond$ 50 citations
\item Fluctuations of anisotropic flow in Pb+Pb collisions at $\sqrt{s_{NN}} = 5.02$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 01 (2020) 051\\
$\diamond$ 49 citations
\item A strategy for a general search for new phenomena using data-derived signal regions and its application within the ATLAS experiment\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 2, 120\\
$\diamond$ 49 citations
\item Correlated long-range mixed-harmonic fluctuations measured in $pp$, $p$+Pb and low-multiplicity Pb+Pb collisions with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 789 (2019) 444-471\\
$\diamond$ 49 citations
\item Measurement of jet fragmentation in 5.02 TeV proton-lead and proton-proton collisions with the ATLAS detector\\
$\diamond$ Published in: Nucl.Phys.A 978 (2018) 65\\
$\diamond$ 48 citations
\item Measurement of jet-substructure observables in top quark, $W$ boson and light jet production in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 08 (2019) 033\\
$\diamond$ 47 citations
\item Measurement of $WW/WZ \rightarrow \ell \nu qq'$ production with the hadronically decaying boson reconstructed as one or two jets in $pp$ collisions at $\sqrt{s} = 8$ TeV with ATLAS, and constraints on anomalous gauge couplings\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 8, 563\\
$\diamond$ 47 citations
\item Measurement of the cross-section and charge asymmetry of $W$ bosons produced in proton–proton collisions at $\sqrt{s} = 8$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 9, 760\\
$\diamond$ 47 citations
\item Search for flavour-changing neutral currents in processes with one top quark and a photon using 81 fb$^{-1}$ of $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS experiment\\
$\diamond$ Published in: Phys.Lett.B 800 (2020) 135082\\
$\diamond$ 47 citations
\item Search for type-III seesaw heavy leptons in dilepton final states in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 3, 218\\
$\diamond$ 47 citations
\item Search for heavy charged long-lived particles in proton-proton collisions at $\sqrt{s} = 13$ TeV using an ionisation measurement with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 788 (2019) 96-116\\
$\diamond$ 47 citations
\item Search for new phenomena with large jet multiplicities and missing transverse momentum using large-radius jets and flavour-tagging at ATLAS in 13 TeV $pp$ collisions\\
$\diamond$ Published in: JHEP 12 (2017) 034\\
$\diamond$ 47 citations
\item Search for large missing transverse momentum in association with one top-quark in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 05 (2019) 041\\
$\diamond$ 47 citations
\item Search for pair production of scalar leptoquarks decaying into first- or second-generation leptons and top quarks in proton–proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 4, 313\\
$\diamond$ 47 citations
\item Evidence for the production of three massive vector bosons with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 798 (2019) 134913\\
$\diamond$ 46 citations
\item Observation of electroweak production of two jets and a Z-boson pair\\
$\diamond$ Published in: Nature Phys. 19 (2023) 2, 237-253\\
$\diamond$ 46 citations
\item Measurements of the production cross-section for a $Z$ boson in association with $b$-jets in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 07 (2020) 044\\
$\diamond$ 46 citations
\item Search for dark matter in association with an energetic photon in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 02 (2021) 226\\
$\diamond$ 46 citations
\item Measurement of the $Z\gamma\rightarrow \nu\bar{nu}\gamma$ production cross section in pp collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector and limits on anomalous triple gauge-boson couplings\\
$\diamond$ Published in: JHEP 12 (2018) 010\\
$\diamond$ 46 citations
\item Search for the electroweak diboson production in association with a high-mass dijet system in semileptonic final states in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 100 (2019) 3, 032007\\
$\diamond$ 46 citations
\item Search for resonances decaying into a weak vector boson and a Higgs boson in the fully hadronic final state produced in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 102 (2020) 11, 112008\\
$\diamond$ 46 citations
\item Search for B-L R -parity-violating top squarks in $\sqrt{s} = 13$ TeV pp collisions with the ATLAS experiment\\
$\diamond$ Published in: Phys.Rev.D 97 (2018) 3, 032003\\
$\diamond$ 45 citations
\item Search for lepton-flavor violation in different-flavor, high-mass final states in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 9, 092008\\
$\diamond$ 45 citations
\item $Z$ boson production in Pb+Pb collisions at $\sqrt{s_{NN}} = 5.02$ TeV measured by the ATLAS experiment\\
$\diamond$ Published in: Phys.Lett.B 802 (2020) 135262\\
$\diamond$ 44 citations
\item Study of the hard double-parton scattering contribution to inclusive four-lepton production in $pp$ collisions at $\sqrt{s} = 8$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 790 (2019) 595-614, Phys.Lett. 790 (2019) 595\\
$\diamond$ 44 citations
\item Measurement of the four-lepton invariant mass spectrum in 13 TeV proton-proton collisions with the ATLAS detector\\
$\diamond$ Published in: JHEP 04 (2019) 048\\
$\diamond$ 43 citations
\item Probing the quantum interference between singly and doubly resonant top-quark production in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.Lett. 121 (2018) 15, 152002\\
$\diamond$ 43 citations
\item Measurement of $W^{\pm}$ boson production in Pb+Pb collisions at $\sqrt{s_{NN}} = 5.02$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 11, 935\\
$\diamond$ 43 citations
\item Measurement of the cross-section for electroweak production of dijets in association with a Z boson in pp collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 775 (2017) 206-228\\
$\diamond$ 43 citations
\item Measurement of differential cross-sections of a single top quark produced in association with a $W$ boson at $\sqrt{s} = 13$ TeV with ATLAS\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 3, 186\\
$\diamond$ 43 citations
\item Study of $WW\gamma$ and $WZ\gamma$ production in $pp$ collisions at $\sqrt{s} = 8$ TeV and search for anomalous quartic gauge couplings with the ATLAS experiment\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 9, 646\\
$\diamond$ 43 citations
\item Search for a heavy Higgs boson decaying into a Z boson and another heavy Higgs boson in the $\ell\ell bb$ and $\ell\ellWW$ final states in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 5, 396\\
$\diamond$ 42 citations
\item Prompt and non-prompt $J/\psi$ elliptic flow in Pb+Pb collisions at $\sqrt{s_{NN}} = 5.02$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 9, 784\\
$\diamond$ 42 citations
\item Combination of the W boson polarization measurements in top quark decays using ATLAS and CMS data at $\sqrt{s} = 8$ TeV\\
$\diamond$ Published in: JHEP 08 (2020) 08, 051\\
$\diamond$ 42 citations
\item Combination of inclusive and differential $t\bar{t}$ charge asymmetry measurements using ATLAS and CMS data at $\sqrt{s} = 7$ and 8 TeV\\
$\diamond$ Published in: JHEP 04 (2018) 033\\
$\diamond$ 42 citations
\item Direct top-quark decay width measurement in the $t\bar{t}$lepton+jets channel at $\sqrt{s} = 8$ TeV with the ATLAS experiment\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 2, 129\\
$\diamond$ 41 citations
\item Observation and Measurement of Forward Proton Scattering in Association with Lepton Pairs Produced via the Photon Fusion Mechanism at ATLAS\\
$\diamond$ Published in: Phys.Rev.Lett. 125 (2020) 26, 261801\\
$\diamond$ 41 citations
\item Measurements of differential cross sections of top quark pair production in association with jets in $pp$ collisions at $\sqrt{s} = 13$ TeV using the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2018) 159\\
$\diamond$ 41 citations
\item Measurements of the inclusive and differential production cross sections of a top-quark–antiquark pair in association with a Z boson at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 8, 737, Eur.Phys.J.C 81 (2021) 737\\
$\diamond$ 41 citations
\item Alignment of the ATLAS Inner Detector in Run-2\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 12, 1194\\
$\diamond$ 41 citations
\item Search for R-parity-violating supersymmetric particles in multi-jet final states produced in 
$p-p$ collisions at $\sqrt{s} = 13$ TeV using the ATLAS detector at the LHC\\
$\diamond$ Published in: Phys.Lett.B 785 (2018) 136-158\\
$\diamond$ 41 citations
\item Search for new phenomena in events containing a same-flavour opposite-sign dilepton pair, jets, and large missing transverse momentum in $\sqrt{s} = 13$ $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 3, 144\\
$\diamond$ 41 citations
\item Search for top squarks decaying to tau sleptons in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 3, 032008\\
$\diamond$ 41 citations
\item Measurements of top-quark pair single- and double-differential cross-sections in the all-hadronic channel in $pp$ collisions at $\sqrt{s} = 13$ TeV using the ATLAS detector\\
$\diamond$ Published in: JHEP 01 (2021) 033\\
$\diamond$ 40 citations
\item Search for heavy resonances decaying to a photon and a hadronically decaying $Z/W/H$ boson in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 3, 032015\\
$\diamond$ 40 citations
\item Search for Higgs boson decays into two new low-mass spin-0 particles in the $4b$ channel with the ATLAS detector using $pp$ collisions at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Phys.Rev.D 102 (2020) 11, 112006\\
$\diamond$ 40 citations
\item Analysis of the $Wtb$ vertex from the measurement of triple-differential angular decay rates of single top quarks produced in the $t$-channel at $\sqrt{s} = 8$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 12 (2017) 017\\
$\diamond$ 40 citations
\item Search for resonances decaying into photon pairs in 139 fb$^{-1}$ of $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 822 (2021) 136651\\
$\diamond$ 40 citations
\item Optimisation of large-radius jet reconstruction for the ATLAS detector in 13 TeV proton–proton collisions\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 4, 334\\
$\diamond$ 40 citations
\item Search for Displaced Leptons in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS Detector\\
$\diamond$ Published in: Phys.Rev.Lett. 127 (2021) 5, 051802\\
$\diamond$ 39 citations
\item Measurement of the azimuthal anisotropy of charged-particle production in $Xe + Xe$ collisions at $\sqrt{s_{NN}} = 5.44$  with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.C 101 (2020) 2, 024906\\
$\diamond$ 39 citations
\item Measurements of differential cross-sections in four-lepton events in 13 TeV proton-proton collisions with the ATLAS detector\\
$\diamond$ Published in: JHEP 07 (2021) 005\\
$\diamond$ 38 citations
\item Operation and performance of the ATLAS Tile Calorimeter in Run 1\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 12, 987\\
$\diamond$ 37 citations
\item Search for squarks and gluinos in final states with one isolated lepton, jets, and missing transverse momentum at $\sqrt{s} = 13$  with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 7, 600, Eur.Phys.J.C 81 (2021) 10, 956 (erratum)\\
$\diamond$ 37 citations
\item Search for new phenomena using the invariant mass distribution of same-flavour opposite-sign dilepton pairs in events with missing transverse momentum in $\sqrt{s} = 13$ TeV pp collisions with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 8, 625\\
$\diamond$ 37 citations
\item Measurement of the suppression and azimuthal anisotropy of muons from heavy-flavor decays in Pb+Pb collisions at $\sqrt{s_{NN}} = 2.76$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.C 98 (2018) 4, 044905\\
$\diamond$ 37 citations
\item Longitudinal Flow Decorrelations in Xe+Xe Collisions at $\sqrt{s_{NN}} = 5.44$ TeV with the ATLAS Detector\\
$\diamond$ Published in: Phys.Rev.Lett. 126 (2021) 12, 122301\\
$\diamond$ 36 citations
\item Measurements of Higgs bosons decaying to bottom quarks from vector boson fusion production with the ATLAS experiment at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 6, 537\\
$\diamond$ 36 citations
\item Measurement of azimuthal anisotropy of muons from charm and bottom hadrons in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.Lett. 124 (2020) 8, 082301\\
$\diamond$ 36 citations
\item Differential cross-section measurements for the electroweak production of dijets in association with a $Z$ boson in proton–proton collisions at ATLAS\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 2, 163\\
$\diamond$ 36 citations
\item Search for direct top squark pair production in events with a Higgs or $Z$ boson, and missing transverse momentum in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: JHEP 08 (2017) 006\\
$\diamond$ 35 citations
\item Measurements of inclusive and differential cross-sections of combined $t\bar{t}\gamma$ and $tW\gamma$ production in the $e\mu$ channel at 13 TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 09 (2020) 049\\
$\diamond$ 35 citations
\item Observation of photon-induced $W^{+}W^{-}$ production in $pp$ collisions at $\sqrt{s} = 13$ TeV using the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 816 (2021) 136190\\
$\diamond$ 35 citations
\item Dijet azimuthal correlations and conditional yields in pp and p+Pb collisions at sNN=5.02TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.C 100 (2019) 3, 034903\\
$\diamond$ 35 citations
\item Search for supersymmetry in events with four or more charged leptons in 139 fb$^{-1}$ of $\sqrt{s} = 13$ TeV pp collisions with the ATLAS detector\\
$\diamond$ Published in: JHEP 07 (2021) 167\\
$\diamond$ 35 citations
\item Measurement of azimuthal anisotropy of muons from charm and bottom hadrons in Pb+Pb collisions at $\sqrt{s_{NN}} = 5.02$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 807 (2020) 135595\\
$\diamond$ 34 citations
\item Measurement of the inclusive and fiducial $t\bar{t}$ production cross-sections in the lepton+jets channel in $pp$ collisions at $\sqrt{s} = 8$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 487\\
$\diamond$ 34 citations
\item Search for vector-boson resonances decaying to a top quark and bottom quark in the lepton plus jets final state in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 788 (2019) 347-370\\
$\diamond$ 34 citations
\item Measurement of $ZZ$ production in the $\ell\ell\nu\nu$ final state with the ATLAS detector in $pp$ collisions at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: JHEP 10 (2019) 127\\
$\diamond$ 34 citations
\item Search for heavy long-lived multicharged particles in proton-proton collisions at $\sqrt{s} = 13$ TeV using the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 99 (2019) 5, 052003\\
$\diamond$ 34 citations
\item Properties of jet fragmentation using charged particles measured with the ATLAS detector in $pp$ collisions at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Phys.Rev.D 100 (2019) 5, 052011\\
$\diamond$ 34 citations
\item Search for dark matter produced in association with a single top quark in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 860\\
$\diamond$ 33 citations
\item Measurement of the production cross section of three isolated photons in $pp$ collisions at $\sqrt{s} = 8$ TeV using the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 781 (2018) 55-76\\
$\diamond$ 33 citations
\item Search for scalar resonances decaying into $\mu^{+}\mu^{-}$ in events with and without $b$-tagged jets produced in proton-proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 07 (2019) 117\\
$\diamond$ 33 citations
\item Exclusive dimuon production in ultraperipheral Pb+Pb collisions at $\sqrt{s_{NN}} = 5.02$ TeV with ATLAS\\
$\diamond$ Published in: Phys.Rev.C 104 (2021) 024906\\
$\diamond$ 33 citations
\item Search for new phenomena in final states with large jet multiplicities and missing transverse momentum using $\sqrt{s} = 13$ TeV proton-proton collisions recorded by ATLAS in Run 2 of the LHC\\
$\diamond$ Published in: JHEP 10 (2020) 062\\
$\diamond$ 33 citations
\item Evidence for electroweak production of two jets in association with a $Z\gamma$ pair in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 803 (2020) 135341\\
$\diamond$ 33 citations
\item Search for Higgs Boson Decays into a $Z$ Boson and a Light Hadronically Decaying Resonance Using 13 TeV $pp$ collision Data from the ATLAS Detector\\
$\diamond$ Published in: Phys.Rev.Lett. 125 (2020) 22, 221802\\
$\diamond$ 33 citations
\item Measurement of colour flow using jet-pull observables in $t\bar{t}$events with the ATLAS experiment at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 10, 847\\
$\diamond$ 32 citations
\item Reconstruction and identification of boosted di-$\tau$ systems in a search for Higgs boson pairs using 13 TeV proton-proton collision data in ATLAS\\
$\diamond$ Published in: JHEP 11 (2020) 163\\
$\diamond$ 32 citations
\item Measurement of dijet azimuthal decorrelations in $pp$ collisions at $\sqrt{s} = 8$ TeV with the ATLAS detector and determination of the strong coupling\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 9, 092004\\
$\diamond$ 32 citations
\item Measurement of angular and momentum distributions of charged particles within and around jets in Pb+Pb and $pp$ collisions at $\sqrt{s_{NN}} = 5.02$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.C 100 (2019) 6, 064901, Phys.Rev.C 101 (2020) 5, 059903 (erratum)\\
$\diamond$ 32 citations
\item Measurement of detector-corrected observables sensitive to the anomalous production of events with jets and large missing transverse momentum in $pp$ collisions at $\sqrt{s} = 13$ TeV using the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 77 (2017) 11, 765\\
$\diamond$ 31 citations
\item Measurement of the $Z(\rightarrow \ell^{+}\ell^{-})\gamma$ production cross-section in$pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 03 (2020) 054\\
$\diamond$ 30 citations
\item Search for dijet resonances in events with an isolated charged lepton using $\sqrt{s} = 13$ TeV proton-proton collision data collected by the ATLAS detector\\
$\diamond$ Published in: JHEP 06 (2020) 151\\
$\diamond$ 30 citations
\item The ATLAS inner detector trigger performance in pp collisions at 13 TeV during LHC Run 2\\
$\diamond$ Published in: Eur.Phys.J.C 82 (2022) 3, 206, Eur.Phys.J.C 82 (2022) 206\\
$\diamond$ 30 citations
\item A search for lepton-flavor-violating decays of the $Z$ boson into a $\tau$-lepton and a light lepton with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 98 (2018) 092010\\
$\diamond$ 29 citations
\item Transverse momentum and process dependent azimuthal anisotropies in $\sqrt{s_{NN}} = 8.16$ TeV $p$+Pb collisions with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 1, 73\\
$\diamond$ 28 citations
\item Search for dark matter in events with missing transverse momentum and a Higgs boson decaying into two photons in pp collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2021) 013\\
$\diamond$ 28 citations
\item Measurements of $W^{+}W^{-} + \ge 1$ jet production cross-sections in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 06 (2021) 003\\
$\diamond$ 28 citations
\item Two-particle azimuthal correlations in photonuclear ultraperipheral Pb+Pb collisions at 5.02 TeV with ATLAS\\
$\diamond$ Published in: Phys.Rev.C 104 (2021) 1, 014903\\
$\diamond$ 27 citations
\item Search for direct production of electroweakinos in final states with missing transverse momentum and a Higgs boson decaying into photons in pp collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 10 (2020) 005\\
$\diamond$ 27 citations
\item Measurement of prompt photon production in $\sqrt{s_{NN}} = 8.16$ TeV $p$-Pb collisions with ATLAS\\
$\diamond$ Published in: Phys.Lett.B 796 (2019) 230-252\\
$\diamond$ 27 citations
\item Search for squarks and gluinos in final states with hadronically decaying $\tau$-leptons, jets, and missing transverse momentum using $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 99 (2019) 1, 012009\\
$\diamond$ 27 citations
\item Search for new phenomena in high-mass final states with a photon and a jet from $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 2, 102\\
$\diamond$ 27 citations
\item Measurement of the inclusive cross-section for the production of jets in association with a Z boson in proton-proton collisions at 8 TeV using the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 10, 847\\
$\diamond$ 26 citations
\item A search for resonances decaying into a Higgs boson and a new particle $X$ in the $XH \rightarrow qqbb$ final state with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 779 (2018) 24-45\\
$\diamond$ 26 citations
\item Determination of the parton distribution functions of the proton from ATLAS measurements of differential $W^{\pm}$ and $Z$ boson production in association with jets\\
$\diamond$ Published in: JHEP 07 (2021) 223\\
$\diamond$ 26 citations
\item Measurement of differential cross sections of isolated-photon plus heavy-flavour jet production in pp collisions at $\sqrt{s} = 8$ TeV using the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 776 (2018) 295-317\\
$\diamond$ 26 citations
\item Performance of the ATLAS Level-1 topological trigger in Run 2\\
$\diamond$ Published in: Eur.Phys.J.C 82 (2022) 1, 7\\
$\diamond$ 25 citations
\item Modelling radiation damage to pixel sensors in the ATLAS detector\\
$\diamond$ Published in: JINST 14 (2019) 06, P06012\\
$\diamond$ 25 citations
\item Measurement of the ratio of cross sections for inclusive isolated-photon production in $pp$ collisions at $\sqrt{s} = 13$ and 8 TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 04 (2019) 093\\
$\diamond$ 25 citations
\item Measurement of $b$-hadron pair production with the ATLAS detector in proton-proton collisions at $\sqrt{s} = 8$ TeV\\
$\diamond$ Published in: JHEP 11 (2017) 062\\
$\diamond$ 24 citations
\item Measurement of the inclusive isolated-photon cross section in $pp$ collisions at $\sqrt{s} = 13$ TeV using 36 fb$^{-1}$ of ATLAS data\\
$\diamond$ Published in: JHEP 10 (2019) 203\\
$\diamond$ 23 citations
\item Evidence for Higgs boson decays to a low-mass dilepton system and a photon in pp collisions at s=13 TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 819 (2021) 136412\\
$\diamond$ 22 citations
\item Search for the Production of a Long-Lived Neutral Particle Decaying within the ATLAS Hadronic Calorimeter in Association with a $Z$ Boson from $pp$ collisions at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Phys.Rev.Lett. 122 (2019) 15, 151801\\
$\diamond$ 22 citations
\item A search for pairs of highly collimated photon-jets in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 99 (2019) 1, 012008\\
$\diamond$ 21 citations
\item Configuration and performance of the ATLAS $b$-jet triggers in Run 2\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 12, 1087\\
$\diamond$ 21 citations
\item Measurement of $J/\psi$ production in association with a $W^{\pm}$ boson with pp data at 8 TeV\\
$\diamond$ Published in: JHEP 01 (2020) 095\\
$\diamond$ 20 citations
\item Search for charged-lepton-flavour violation in $Z$-boson decays with the ATLAS detector\\
$\diamond$ Published in: Nature Phys. 17 (2021) 7, 819-825\\
$\diamond$ 20 citations
\item Measurement of the jet mass in high transverse momentum $Z(\rightarrow b\bar{b})\gamma$ production at $\sqrt{s} = 13$ TeV using the ATLAS detector\\
$\diamond$ Published in: Phys.Lett.B 812 (2021) 135991\\
$\diamond$ 20 citations
\item Medium-Induced Modification of $Z$-Tagged Charged Particle Yields in $Pb+Pb$ Collisions at 5.02 TeV with the ATLAS Detector\\
$\diamond$ Published in: Phys.Rev.Lett. 126 (2021) 7, 072301\\
$\diamond$ 19 citations
\item Measurement of the $k_{t}$ splitting scales in $Z\rightarrow\ell\ell$ events in $pp$ collisions at $\sqrt{s} = 8$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 08 (2017) 026\\
$\diamond$ 19 citations
\item Search for Dark Matter Produced in Association with a Dark Higgs Boson Decaying into $W^{\pm}W^{\mp}$ or $ZZ$ in Fully Hadronic Final States from $\sqrt{s} = 13$ TeV pp Collisions Recorded with the ATLAS Detector\\
$\diamond$ Published in: Phys.Rev.Lett. 126 (2021) 12, 121802\\
$\diamond$ 18 citations
\item Properties of $g\rightarrow b\bar{b}$ at small opening angles in $pp$ collisions with the ATLAS detector at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: Phys.Rev.D 99 (2019) 5, 052004\\
$\diamond$ 18 citations
\item Measurement of distributions sensitive to the underlying event in inclusive $Z$-boson production in pp collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 8, 666\\
$\diamond$ 18 citations
\item Measurement of long-range two-particle azimuthal correlations in $Z$-boson tagged $pp$ collisions at $\sqrt{s} = 8$ and 13 TeV\\
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 1, 64\\
$\diamond$ 18 citations
\item Constraints on Higgs boson properties using $WW^{*}(\rightarrow\nu\mu\nu)jj$ production in 36.1fb$^{-1}$ of $\sqrt{s} = 13$ TeV pp collisions with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 82 (2022) 7, 622\\
$\diamond$ 17 citations
\item Measurement of hadronic event shapes in high-$p_{T}$ multijet final states at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 01 (2021) 188, JHEP 12 (2021) 053 (erratum)\\
$\diamond$ 16 citations
\item Search for phenomena beyond the Standard Model in events with large $b$-jet multiplicity using the ATLAS detector at the LHC\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 1, 11, Eur.Phys.J.C 81 (2021) 3, 249 (erratum)\\
$\diamond$ 16 citations
\item Search for top squarks in events with a Higgs or $Z$ boson using 139 fb$^{-1}$ of $pp$ collision data at $\sqrt{s} = 13$ TeV with the ATLAS detector
$\diamond$ Published in: Eur.Phys.J.C 80 (2020) 11, 1080\\
$\diamond$ 15 citations
\item Resolution of the ATLAS muon spectrometer monitored drift tubes in LHC Run 2\\
$\diamond$ Published in: JINST 14 (2019) 09, P09011\\
$\diamond$ 15 citations
\item A search for the decays of stopped long-lived particles at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 07 (2021) 173\\
$\diamond$ 15 citations
\item Measurement of $W^{\pm}$-boson and Z-boson production cross-sections in pp collisions at $\sqrt{s} = 2.76$ with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 11, 901\\
$\diamond$ 14 citations
\item Search for Higgs boson production in association with a high-energy photon via vector-boson fusion with decay into bottom quark pairs at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 03 (2021) 268\\
$\diamond$ 14 citations
\item Measurement of single top-quark production in association with a $W$ boson in the single-lepton channel at $\sqrt{s} = 8$ with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 81 (2021) 8, 720\\
$\diamond$ 14 citations
\item Measurement of $\tau$ polarisation in $Z/\gamma^{*} \rightarrow \tau\tau$ decays in proton–proton collisions at $\sqrt{s} = 8$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 78 (2018) 2, 163\\
$\diamond$ 13 citations
\item Measurement of the relative $B^{\pm}_{c}/B^{\pm}$ production cross section with the ATLAS detector at $\sqrt{s} = 8$ TeV
$\diamond$ Published in: Phys.Rev.D 104 (2021) 1, 012010\\
$\diamond$ 13 citations
\item Search for trilepton resonances from chargino and neutralino pair production in $\sqrt{s} = 13$ TeV $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 103 (2021) 11, 112003\\
$\diamond$ 12 citations
\item Performance of the ATLAS RPC detector and Level-1 muon barrel trigger at $\sqrt{s} = 13$ TeV\\
$\diamond$ Published in: JINST 16 (2021) 07, P07029\\
$\diamond$ 12 citations
\item Measurement of differential cross sections for single diffractive dissociation in $\sqrt{s} = 8$ TeV $pp$ collisions using the ATLAS ALFA spectrometer\\
$\diamond$ Published in: JHEP 02 (2020) 042, JHEP 10 (2020) 182 (erratum)\\
$\diamond$ 12 citations
\item The ATLAS Fast TracKer system\\
$\diamond$ Published in: JINST 16 (2021) P07006\\
$\diamond$ 11 citations
\item Emulating the impact of additional proton–proton interactions in the ATLAS simulation by presampling sets of inelastic Monte Carlo events\\
$\diamond$ Published in: Comput.Softw.Big Sci. 6 (2022) 1, 3\\
$\diamond$ 11 citations
\item Study of ordered hadron chains with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 96 (2017) 9, 092008\\
$\diamond$ 11 citations
\item Measurement of isolated-photon plus two-jet production in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: JHEP 03 (2020) 179\\
$\diamond$ 11 citations
\item Comparison between simulated and observed LHC beam backgrounds in the ATLAS experiment at $E_{beam} = 4$ TeV\\
$\diamond$ Published in: JINST 13 (2018) 12, P12006\\
$\diamond$ 10 citations
\item Search for bottom-squark pair production in $pp$ collision events at $\sqrt{s} = 13$ TeV with hadronically decaying $\tau$-leptons, $b$-jets and missing transverse momentum using the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 104 (2021) 3, 032014\\
$\diamond$ 9 citations
\item Search for excited electrons singly produced in proton–proton collisions at $\sqrt{s} = 13$ TeV with the ATLAS experiment at the LHC\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 9, 803\\
$\diamond$ 9 citations
\item Measurements of sensor radiation damage in the ATLAS inner detector using leakage currents\\
$\diamond$ Published in: JINST 16 (2021) P08025\\
$\diamond$ 8 citations
\item Performance of the upgraded PreProcessor of the ATLAS Level-1 Calorimeter Trigger\\
$\diamond$ Published in: JINST 15 (2020) 11, P11016\\
$\diamond$ 8 citations
\item Measurement of $K^{0}_{s} and \Lambda^{0}$ production in $t\bar{t}$ dileptonic events in pp collisions at $\sqrt{s} = 7$ TeV with the ATLAS detector\\
$\diamond$ Published in: Eur.Phys.J.C 79 (2019) 12, 1017\\
$\diamond$ 6 citations
\item Measurements of jet observables sensitive to $b$-quark fragmentation in $t\bar{t}$ events at the LHC with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.D 106 (2022) 3, 032008\\
$\diamond$ 5 citations
\item Two-particle Bose–Einstein correlations in $pp$ collisions at $\sqrt{s} = 13$ TeV measured with the ATLAS detector at the LHC\\
$\diamond$ Published in: Eur.Phys.J.C 82 (2022) 7, 608\\
$\diamond$ 5 citations
\item Search for heavy resonances decaying into a photon and a hadronically decaying Higgs boson in $pp$ collisions at $\sqrt{s} = 13$ TeV with the ATLAS detector\\
$\diamond$ Published in: Phys.Rev.Lett. 125 (2020) 251802\\
$\diamond$ 5 citations
\item Evidence for the production of three massive vectorbosons in $pp$ collisions with the ATLAS detector\\
$\diamond$ Published in: PoS DIS2019 (2019) 135\\
$\diamond$ 1 citation




\end{itemize}
\textbf{Academia Sinica}: 3 publications\\
\textrm{Name on the Publication: }\textbf{Y.T. Shen (Taiwan, Inst. Phys.)}\\
\begin{itemize}
    \item Characterization and Performance of Germanium Detectors with sub-keV Sensitivities for Neutrino and Dark Matter Experiments\\
    $\diamond$ Published in: Nucl.Instrum.Meth.A 836 (2016) 67-82\\
    $\diamond$ 85 citations
    \item Differentiation of Bulk and Surface Events in p-type Point-Contact Germanium Detectors for Light WIMP Searches\\
    $\diamond$ Published in: Astropart.Phys. 56 (2014) 1-8\\
    $\diamond$ 48 citations
    \item Limits on spin-independent couplings of WIMP dark matter with a p-type point-contact germanium detector\\
    $\diamond$ Published in: Phys.Rev.Lett. 110 (2013) 26, 261301\\
    $\diamond$ 90 citations
\end{itemize}
\textbf{National Taiwan University}: 6 publications\\
\textrm{Name on the Publication: }\textbf{Y.-T. Shen (Taiwan, Natl. Taiwan U.)} and \textbf{Y.T. Shen (Taiwan, Natl. Taiwan U.)}\\
\begin{itemize}
    \item The Physics of the B Factories\\
    $\diamond$ Published in: Eur.Phys.J.C 74 (2014) 3026\\
    $\diamond$ 622 citations
    \item Study of B $\rightarrow$ phi phi K Decays\\
    $\diamond$ Published in: e-Print: 0802.1547 [hep-ex]\\
    $\diamond$ 6 citations
    \item Measurement of $D^{0} - \bar{D}^{0}$ Mixing Parameters in $D^{0} \rightarrow K^{0}_{s}\pi^{+}\pi^{-}$ decays\\
    $\diamond$ Published in: Phys.Rev.Lett. 99 (2007) 131803\\
    $\diamond$ 232 citations
    \item Improved measurement of CP-violating parameters in B0 $\rightarrow$ rho+ rho- decays\\
    $\diamond$ Published in: Phys.Rev.D 76 (2007) 011104\\
    $\diamond$ 71 citations
    \item Measurement of the absolute branching fraction of the D+-(s) meson\\
    $\diamond$ Contribution to: ICHEP 2006 conference\\
    $\diamond$ 10 citations
    \item Observation of B $\rightarrow$ phi phi K Decays\\
    $\diamond$ Contribution to: ICHEP 2006 conference\\
    $\diamond$ 2 citations
\end{itemize}


\end{resume}
\end{document}
