\documentclass[12pt,letterpaper]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt')
                                                   % paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') 
% moderncv themes
\moderncvstyle{classic}           % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green}             % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[utf8]{inputenc}       % use UTF-8 input encoding
\usepackage{ragged2e}             % Text alignment
\usepackage[scale=0.75]{geometry} % adjust the page margins

% Change font
\renewcommand{\familydefault}{\sfdefault} % use serif

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% VARIABLES
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\CompanyName}{Company}
% \newcommand{\CompanyAddress}{City, State}
\newcommand{\CompanyAddress}{San Francisco, CA}
\newcommand{\JobPositionName}{Data Scientist}
\newcommand{\ManagerName}{Madam or Sir to whom it may concern:}
\newcommand{\ClosingWords}{Yours faithfully,} % 非以對方姓氏稱呼對方時
%\newcommand{\ClosingWords}{Yours sincerely,} % 知道對方姓氏時

\newcommand{\MyFirstName}{Yu-Ting}
\newcommand{\MyLastName}{Shen}
\newcommand{\MyAddress}{Norman, OK 73019}
\newcommand{\MyPhoneNumber}{(450)200.2633}
\newcommand{\MyEmail}{YuTing.Shen-1@ou.edu}
%\newcommand{\MyHomepage}{www.myhomepage.com}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% PERSONAL DATA
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\name{\MyFirstName{}}{\MyLastName{}}
\address{\MyAddress{}}
\phone[mobile]{\MyPhoneNumber{}} % can be mobile, fixed, fax
\email{\MyEmail{}}



\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% RECIPIENT DATA
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\recipient{\CompanyName{}}{\CompanyAddress{}}
\date{\today}
\opening{Dear \ManagerName{}}
\closing{\ClosingWords}
\makelettertitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% LETTER CONTENTS
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\justifying

% USE A SENTENCE TO DESCRIBE THE REASON WHY APPLYING FOR THIS POSITION AT HERE.
I am applying for the position of \JobPositionName{} in \CompanyName{}.
I started to analyze big data since I enrolled in my Ph.D program and prepared myself to work with big data by learning necessary knowledge and skills.

I have taken several data analysis and machine learning courses and a data science bootcamp.
The skills such as querying data using SQL, manipulating and cleaning data using Pandas, visualizing data distributions using Matplotlib and Seaborn, and machine learning using Scikit-learn and Keras are in my toolbox now.
Now I participate in the competitions on Kaggle to sharpen my data analysis skills and learn from other experts.

The Ph.D. in high energy physics trained me to be a careful researcher and strengthened my problem solving skills.
Presenting the findings in weekly meetings gave me the ability to explain quantitative topics for a variety of audiences.
Analyzing the experimental data which are produced at a rate about 25 GB/s enhanced my C/C++ and Python programming skills.
%In high energy physics, we analyze the experimental data and compare the results with the theoretical predictions.
%The experimental raw data are produced at a rate about 50 TB/s.
%In order to analyze the huge amount of data produced by the experiment, I developed an analysis framework using C/C++ and Python.

I would welcome the chance to speak with you about the responsibilities of the \JobPositionName{} position.
My resume containing detailed work experience and education is attached.
I am confident that my background makes me a unique candidate to fit this challenging position and I would be a valuable addition to your team.
I look forward to hearing from you.
Thank you for your consideration.

\vspace{0.5cm}

\makeletterclosing

\end{document}
